\renewcommand{\theequation}{\theenumi}
\begin{enumerate}[label=\arabic*.,ref=\thesubsection.\theenumi]
\numberwithin{equation}{enumi}

\item Let $\vec{P}$ be the point on the parabola
\begin{equation}
\label{eq:parab_circ_parab}
\vec{x}^T\myvec{0 & 0 \\ 0 & 1}\vec{x} -\myvec{8 & 0 }\vec{x} 
 = 0
\end{equation}
which is at a minimum distance from the centre $\vec{C}$ of the circle
\begin{equation}
\label{eq:parab_circ_circ}
\vec{x}^T\vec{x} +\myvec{0 & 12 }\vec{x} 
 = 1 
\end{equation} 
Find the equation of the circle passing through $\vec{C}$ and having its centre at $\vec{P}$. 
\item Let $\vec{P}$ 
be a point on the parabola
\begin{equation}
\vec{x}^T\myvec{1 & 0 \\ 0 & 0}\vec{x} +\myvec{0 & 4 }\vec{x} 
 = 0
\end{equation}
%%
Given that the distance of $\vec{P}$ from the centre of the circle
\begin{equation}
\vec{x}^T\vec{x} +\myvec{6 \\ 0 }\vec{x} + 8 = 0
\end{equation}
%
is minimum.  Find the equation of the tangent to the parabola at $\vec{P}$.
\item Find the eccentricity of the hyperbola whose length of the latus rectum is equal to 8 and the length of 
its conjugate axis is equal to half the distance between its foci. 
\item $\vec{P}$ and $\vec{Q}$ are two distinct points on the parabola
\begin{equation}
\vec{x}^T\myvec{0 & 0 \\ 0 & 1}\vec{x} -\myvec{4 & 0 }\vec{x} 
 = 0
\end{equation}
with parameters $t$ and $t_1$ respectively.  If the normal at $\vec{P} $ passes through $\vec{Q}$, then find 
the minimum value of $t_1^2$ using a descent algorithm.
\item A tangent at a point on the ellipse 
\begin{equation}
\vec{x}^TV\vec{x} =51
\end{equation}
%
where
\begin{equation}
V = \myvec{3 & 0 \\ 0 & 27}
\end{equation}
%
meets the coordinate axes at  $\vec{A}$  and  $\vec{B}$.  If   $\vec{O}$  be the origin, find the minimum area 
of $\triangle OAB$.
\item Find the shortest distance between the line 
\begin{equation}
\myvec{1 & -1 }\vec{x}  =0
\end{equation}
%
and the curve
\begin{equation}
\vec{x}^T\myvec{0 & 0 \\ 0 & 1}\vec{x} - \myvec{1 & 0}\vec{x} + 2 =0
\end{equation}
\item Let $S$ be the set of all complex numbers $z$ satisfying $\abs{z-2+\j} \ge \sqrt{5}$. If the complex number $z_0$ is such that $\frac{1}{\abs{z_0-1}}$ is the maximum of the set $\cbrak{\frac{1}{\abs{z-1}}: z \in S}$, find the principal argument of 
\begin{align}
\frac{4-z_0-\bar{z}_0}{z_0-\bar{z}_0+2\j}
\end{align}
\item Let $\omega \ne 1$ be a cube root of unity. Find the minimum of the set
\begin{align}
\abs{a+b\omega+c\omega^2}, 
\end{align}
%
where $a,b,c$ are distinct nonzero integers.
\item Let 
\begin{align}
\label{eq:mat_def}
\vec{M} = \myvec{\sin^4\theta & -1-\sin^2\theta \\ 1+ \cos^2\theta & \cos^4\theta} = \alpha\vec{I} + \beta \vec{M}^{-1}
\end{align}
where $\alpha, \beta$ are real functions of $\theta$ and $\vec{I}$ is the identity matrix. If 
\begin{align}
\alpha^{*} &= \min_{\theta}\alpha\brak{\theta}
\\
\beta^{*} &= \min_{\theta}\beta\brak{\theta}, 
\end{align}
find $\alpha^{*} + \beta^{*}$.
\item Find the minimum value of 
\begin{align}
\cos \brak{P+Q}
\cos \brak{Q+R}
\cos \brak{R+P}
\end{align}
%
in $\triangle PQR$.
\item Find the minimum value of $\alpha$ for which 
\begin{align}
4\alpha x^2 + \frac{1}{x} \ge 1, x > 0.
\end{align}
\item Let 
\begin{align}
S = S_1\cap S_2\cap S_3,
\end{align}
%
where
\begin{align}
S_1 &= \cbrak{z\in C: \abs{z}< 4}
\\
S_2 &= \cbrak{z\in C: \Im\sbrak{\frac{z-1+\j\sqrt{3}}{1-\j\sqrt{3}}}},
\\
S_3 &= \cbrak{z\in C: \Re\brak{z} > 0}
\end{align}
Find
\begin{align}
\min_{z\in S}\abs{1-3\j-z}
\end{align}
\item A line 
\begin{align}
L: \myvec{m -1}\vec{x} = -3
\end{align}
passes through
\begin{align}
\vec{E} = \myvec{0\\3}
\end{align}
and 
\begin{align}
\vec{x}\myvec{0 & 0 \\ 0 & 1}\vec{x} - \myvec{16 & 0}\vec{x} = 0, 0 \le \myvec{0 & 1}\vec{x} \le 6
\end{align}
%
at the point $\vec{F}$.  Find $m$ such that the area of $\triangle EFG$ is maximum.
\item If $\abs{z-3-2j} \le 2$, find
\begin{align}
\min_{z}\abs{2z-6+5\j}
\end{align}
\item Find 
\begin{align}
\max_{z}\abs{Arg\brak{\frac{1}{1-z}}}
\\
s.t\quad \abs{z} = 1, z \ne 1.
\end{align}
\item Find the maximum value of the function 
\begin{align}
f(x) = 2x^3-15x^2+36x-48
\end{align}
on the set 
\begin{align}
A = \cbrak{x : x^2+20 \le 9x}
\end{align}
\item Find the minimum distance of a point on the curve 
\begin{align}
\vec{x}^T\myvec{1 & 0 \\ 0 & 1}\vec{x} + \myvec{0 -1}\vec{x}=4
\end{align}
%
from the origin.
\item Find 
\begin{align}
\min_{z}\abs{z+\frac{1}{2}}
\\
s.t\quad \abs{z} \ge 2
\end{align}
\item Find  the minimum value of
\begin{align}
\tan A + \tan B
\\
s.t \quad A+B=6,
\\
A, B \ge 0
\end{align}
\item Show that 
\begin{multline}
\sin A_1+\sin A_2 + \dots + \sin A_n 
\\
\le n \sin \brak{\frac{A_1+A_2+\dots + A_n}{n}}
\\
0 < A_i < \pi, i = 1, 2, \dots , n, n \ge 1
\end{multline}
\item Let $\vec{F}_1, \vec{F}_2$ be the foci of the standard ellipse with parameters $a$ and $b$.  If $\vec{P}$ be any point on the ellipse, find the maximum area of $\triangle PF_1F_2$.
\item A circle $\norm{\vec{x}}=1$ intersects the $X-$ axis at $\vec{P}$ and $\vec{Q}$.  Another circle with centre $\vec{Q}$ intersects this circle above the $X-$ axis at $\vec{R}$ and the line segent $PQ$ at $\vec{S}$.  Find the maximum area of $\triangle QSR$.
\item Let $\vec{M}$ be a fixed point in the first quadrant.   A line through $\vec{M}$ intersects the positive axes at $\vec{P}, \vec{Q}$ respectively. If $\vec{O}$ be the origin, find the minimum area of $\triangle OPQ$.
\end{enumerate}
