\renewcommand{\theequation}{\theenumi}
\begin{enumerate}[label=\arabic*.,ref=\thesubsection.\theenumi]
\numberwithin{equation}{enumi}
\item Find the remainder when $x^3+3x^2+3x+1$ is divided by 
\begin{enumerate}
\item $x+1$
\item $x-\frac{1}{2}$
\item $x$
\item $x+\pi$
\item $5+2x$
\end{enumerate}
%
\item Check whether $7+3x$ is a factor of $3x^3+7x$.
%
\item Determine which of the following polynomials has $(x+1)$ as a factor:
%
\begin{enumerate}
\item $x^3+x^2+x+1$
\item $x^4+x^3+x^2+x+1$
\item $x^4+3x^3+3x^2+x+1$
\item $x^3-x^2-\brak{2+\sqrt{2}}+\sqrt{2}$.
\end{enumerate}
%
\item Determine whether $g(x)$ is a factor of $p(x)$ in each of the following cases:
%
\begin{enumerate}
\item $p(x) = 2x^3+x^2-2x-1, g(x) = x+1$
\item $p(x) = x^3+3x^2+3x+1, g(x) = x+2$
\item $p(x) = x^4-4x^2+x+6, g(x) = x-3$
\end{enumerate}
%
\item  Factorise : 
\begin{enumerate}
\item $x^3 – 2x^2 – x + 2 $
\item $x^3– 3x^2 – 9x – 5 $
 \item $x^3+ 13x^2 + 32x + 20 $
\item $2y^3+ y^2– 2y – 1$
\end{enumerate}
\item Find the roots of the following equations:
\begin{enumerate}
\item  $x - \frac{1}{x} = 3, x \ne =0 $
\item  $ \frac{1}{x+4} - \frac{1}{x-7} = \frac{11}{30}, x\ne =-4, 7 $
\end{enumerate}
%
\item Find the slope of the tangent to the curve $y = 3x^4-4x$ at $x=4$.
\item Find the slope of the tangent to curve $y = x^3-3x+2$ at the point whose 
x-coordinate is 2.
\item Find the slope of the tangent to the curve $y = x^3-3x+2 $ at the point whose x-coordinate is 3.
\item Find the slope of the normal to the curve 
$
\vec{x} = a \myvec{\cos^3\theta \\ \sin^{3}\theta}
$
at $\theta = \frac{\pi}{4}$.
\item Find the slope of the normal to the curve 
$
\vec{x} =  \myvec{1-a\sin\theta \\ b\cos^{2}\theta}
$
at $\theta = \frac{\pi}{2}$.
\item Find points at which the tangent to the curve $y = x^3-3x^2-9x+7$ is parallel to th x-axis.
\item Find the point on the curve $y = x^3– 11x + 5$
at which the tangent is $\myvec{1 & -1}\vec{x} =  11$.
\item Find the equations of all lines having slope 0 which are tangent to the curve 
$
y = \frac{1}{x^2-2x+3}
$.
\item Find the equations of the tangent and normal to the given curves at the indicated points: 
%
\begin{enumerate}
\item
$
y= x^4 - 6x^3+13x^2-10x+5
$
at \myvec{0\\5}.
\item
$
y = x^4 - 6x^3+13x^2-10x+5
$
at \myvec{1\\3}.
\item
$
y = x^3
$
at \myvec{1\\1}.
\end{enumerate}
%
\item Show that the tangents to the curve $y = 7x^3 + 11$ at the points where $x = 2$ and $x = -2$ are parallel.
\item Find the points on the curve $y = x^3$  at which the slope of the tangent is equal to the y-coordinate of the point.
\item For the curve $y = 4x^3 – 2x^5$ find all the points at which the tangent passes through the origin.
\item Find the equation of the normal at the point $\myvec{am^2 \\ am^3}$  for the curve $ay^2 = x^3$
\item Find the equation of the normals to the curve $y = x^3+2x+6$ which are parallel to the line $\myvec{1 & 14} + 4 = 0$.
\item Find the slope of the normal to the curve $y = 2x^2 + 3 \sin x$ at $x = 0$.
%
Show that the normal at any point $\theta$ to the curve $\vec{x} = \myvec{a \cos\theta + a \theta \sin\theta\\  a \sin\theta – a\theta \cos\theta}$ is at a constant distance from the origin.
%
\item Find the slope of the tangent to the curve $\vec{x} = \myvec{t^2+3t-8 \\ 2t^2-2t-5}$
at the point $\myvec{2\\-1}$.
\item Find the points on the curve $9y^2 = x^3$, where the normal to the curve makes equal intercepts with the axes.
\item Find the area under $y = x^4, x = 1, x = 5$ and x-axis.
%
\item Find the area bounded by the curve $y = x^3, x =-2, x = 1$ and the x-axis.
\item Find the area bounded by the curve $y = x \abs{x}, x = -1, x = 1$ and the x-axis.
\item Find the area bounded by the y-axis, $y = \cos x$ and $y = \sin x$ when $0 \le x \le \frac{\pi}{2}$.\item Show that the function given by $f(x) = 3x+17$  is increasing on $\vec{R}$.
\item Show that the function given by $f(x) = e^{2x}$  is increasing on $\vec{R}$.
%
%
\item Show that the function given by 
\begin{align}
f(x)  = \sin x
\end{align}
%
is 
\begin{enumerate}
\item increasing in $\brak{0,\frac{\pi}{2}}$
\item decreasing in $\brak{\frac{\pi}{2}, \pi}$
\end{enumerate}
%
%
\item Find the intervals in which the function given by 
\begin{align}
f(x)  = 2x^3-3x^2 - 36x +7
\end{align}
%
is 
\begin{enumerate}
\item increasing
\item decreasing.
\end{enumerate}
%
\item Find the intervals in which the following functions are strictly increasing or decreasing
%
\begin{enumerate}
\item $\brak{x+1}^3\brak{x-3}^3$
\item $-2x^3-9x^2-12x+1$
\end{enumerate}
%
\item Show that 
%
\begin{align}
y = \log \brak{1+x}-\frac{2x}{2+x}, x > -1,
\end{align}
%
is an increasing function of $x$ throughout its domain.
%
\item Find the values of $x$ for which $y = x\brak{x-2}^2$ is an increasing function.
%
\item Prove that
%
\begin{align}
y = \frac{4\sin \theta}{2+\cos \theta} - \theta
\end{align}
%
is an incresing function of $\theta$ in $\sbrak{0,\frac{\pi}{2}}$.
\item Prove that the logarithmic function is increasing on $\brak{0, \infty}$.
\item Which of the following functions are decreasing on $\sbrak{0,\frac{\pi}{2}}$?
%
\begin{enumerate}
\item $\cos x$
\item $\cos 2x$
\item $\cos 3x$
\item $\tan x$
\end{enumerate}
%
\item Find the intervals on which 
%
\begin{align}
f(x) = x^{100}+\sin x -1
\end{align}
%
is decreasing.
\item Let $I$ be any interval disjoint from $\sbrak{1,-1}$.  Prove that the function $f$ given by $f(x) = x +\frac{1}{x}$ is increasing on $I$.
\item Prove that the function $f$ given by $f(x) = \log \sin x$ is increasing on $\brak{0,\frac{\pi}{2}}$ and decreasing on $\brak{\frac{\pi}{2}, \pi}$.
\item Prove that the function $f$ given by $f(x) = \log \abs{\cos x}$ is decreasing on $\brak{0,\frac{\pi}{2}}$ and increasing on $\brak{\frac{3\pi}{2}, 2\pi}$.
\item Prove that the function given by $f(x) = x^3-3x^2+3x-100$ is increasing in $\vec{R}$.
\item Find the interval(s) in which $f(x) = x^2e^{-x}$ is increasing.
\item Find the maximum and minimum values, if any, of $g(x) = x^3+1$.
%
\item Find the maximum and minimum values, if any of
the following functions given by 
%
\begin{enumerate}
\item $h(x) = \sin\brak{2x} + 5$
\item $f(x) = \abs{\sin\brak{4x} + 3}$
\end{enumerate}
%
\item Find the local maximum and minima, if any, of
the following functions.  Find also the  local maximum and local minimum values, as the case may be
%
\begin{enumerate}
\item $g(x) = x^3-3x$
\item $h(x) = \sin x +\cos x, x \in \brak{0,\frac{\pi}{2}}$
\item $f(x) = \sin x -\cos x, x \in \brak{0,2\pi}$
\item $f(x) = x^3-6x^2+9x+15$
\item $g(x) = \frac{x}{2} + \frac{2}{x}, x > 0$
\item $g(x) = \frac{1}{x^2+2}$
\item $f(x) = x\sqrt{1-x}, 0 < x < 1$.
\end{enumerate}
%
\item Prove that the following functions do not have maxima or minima:
%
\begin{enumerate}
\item $f(x) = e^x$
\item $g(x) = \log x$
\item $h(x) = x^3+x^2+x+1$
\end{enumerate}
\item Find the absolute maximum and absoute minimum value of the following functions in the given intervals
%
\begin{enumerate}
\item $f(x) = x^3, x \in \brak{-2,2}$
\item $f(x) = \sin x + \cos x,  x \in \brak{0,\pi}$.
\end{enumerate}
%
\item Find both the maximum value and the minimum value of 
\begin{align}
3x^4-8x^3+12x^2-48x+25, x \in \sbrak{0,3}.
\end{align}
%
\item At what points in the interval $\sbrak{0,2\pi}$, does the function $\sin 2x$ attain its maximum value?
\item What is the maximum value of the function $\sin x + \cos x$?
\item Find the maximum value of $2x^3-24x+107$ in the interval $\sbrak{1,3}$.  Find the maximum value of the same function in $\sbrak{-3,1}$.
\item It is given that at $x=1$, the function $x^4-62x^2 + ax+9$ attains its maximum value on the interval $\sbrak{0,2}$.  Find the value of $a$.
\item Find the maximum and minimum values of $x + \sin 2x$ on $\sbrak{0, 2\pi}$.
\item For all real values of x, the minimum value of
\begin{align}
\frac{1-x+x^2}{1+x+x^2}.
\end{align}
%
\item Find the maximum value of 
\begin{align}
\sbrak{x\brak{x-1}}^{\frac{1}{3}}.
\end{align}
\item Using differentials, find the approximate value of each of the following
%
\begin{enumerate}
\item $\brak{\frac{17}{81}}^{\frac{1}{4}}$
\item $\brak{33}^{-\frac{1}{5}}$
\end{enumerate}
%
\item Show that the function given by $f(x) = \frac{\log x}{x}$ has maximum at $x = 3$.
\item Find the intervals in which the function $f$ given by 
%
\begin{align}
f(x)  = \frac{4\sin x-2x - x\cos x}{2+\cos x}
\end{align}
%
is
%
\begin{enumerate}
\item increasing 
\item decreasing 
\end{enumerate}
%
\item Find the interals in which the function $f$ given by 
%
\begin{align}
f(x)  = x^3 + \frac{1}{x^3}, \quad x \ne 0
\end{align}
%
is
\begin{enumerate}
\item increasing 
\item decreasing 
\end{enumerate}
%
\item Find the absolute maximum and minimum values of the function $f$ given by 
%
\begin{align}
f(x)  = \cos^2 x + \sin x , \quad x \in \sbrak{0,\pi}
\end{align}
%
\item Find the points at which the function $f$ given by 
%
\begin{align}
f(x)  = \brak{x-2}^4\brak{x+1}^3
\end{align}
%
has
\begin{enumerate}
\item local maxima
\item local minima
\item point of inflexion
\end{enumerate}
%
\end{enumerate}
