\item There are  n - 1 red balls, n green balls and n + 1 blue balls in a bag. The number of ways of chosing two balls from the bag that have different colours is 299. What is the value of n?

\item Let $S(M)$ denote the sum of the digits of a positive integer M written in base 10. Let N be the smallest positive integer such that $S(N) = 2013$. What is the value of $S(5N + 2013)$?

\item Let Akbar and Birbal togeather have n marbles, where $n > 0$. Akbar says to Birbal, " If I give you some marbles then you will have twice as many marbles as I will have." Birbal says to Akbar, " If I give you some marbles then you will have thrice as many marbles as I will have."

\item Carol was given three numbers and was asked to add the largest of the three to the product of the other two. Instead, she multiplied the largest with the sum of other two, but still got the right answer. What is the sum of the three numbers?

\item To each element of the set
\begin{align*}
S = \{1, 2,.........1000\}
\end{align*}
a colour is assigned. Suppose that for any two elements a, b of S, if 15 divides a + b then they are both assigned the same colour. What is the maximum possible number of distinct colours used?

\item Let $m$ be the smallest odd positive integer for which
\begin{align*}
1 + 2 +........+m
\end{align*}
is a square of an integer and let $n$ be the smallest even positive integer for which
\begin{align*}
1 + 2 +........+n 
\end{align*}
is a square of an integer. What is the value of $m + n$?

\item What is the maximum possible value of k for which 2013 can be written as a sum of k consecutive positive integers?

\item What is the sum(in base 10) of all natural numbers less than 64 which have exactly three ones in their base 2 representation?
