\item What is the smallest possible natural number n for which the equation 
\begin{align*}
x^2 - nx + 2014 = 0
\end{align*}
has integer roots?

\item A natural number k is such that 
\begin{align*}
k^2 < 2014 < (k+1)^2
\end{align*}
What is the largest prime factor of k?

\item The first term of a sequence is 2014. Each succeeding term is the sum of the cubes of the digits of the previous term. What is the $2014^{th}$ of the sequence?

\item In a triangle with integer side lengths, one side is three times as long as a second side, and the length of the third side is 17. What is the greatest possible perimeter of the triangle? 

\item Let S be a set of real numbers with mean M. If the means of the sets $S \cup \{15\}$ and $S \cup \{15,1\}$ are M+2 and M + 1, respectively, then how many elements does S have?

\item For how many natural numbers n between 1 and 2014 (both inclusive) is $\frac{8n}{9999-n}$ an integer?


\item Let f be a one-to-one function from the set of natural numbers to itself such that f(mn) = f(m)f(n) for all natural numbers m and n. What is the least possible value of f(999)?


\item What is the number of ordered pairs (A, B) where A and B are subsets of $\{1,2,...,5\}$ such that neither 
$A \subseteq B$ nor $B \subseteq A$?

\item Natural numbers k, l, p and q are such that if a and b are roots of 
\begin{align*}
x^2 - kx + 1 = 0
\end{align*}
then $a + \frac{1}{b}$ and $b + \frac{1}{a}$ are the roots of 
\begin{align*}
x^2 - px + q = 0
\end{align*}
What is the sum of all possible values of q?

\item For natural numbers x and y, let(x, y) denote the greatest common divisor of x and y. How many pairs of natural numbers x and y with $x \leq y$ satisfy the equation xy = x + y + (x, y)?

\item For a natural number b, let N(b) denote the number of natural numbers a for which the equation 
\begin{align*}
x^2 + a x + b = 0
\end{align*}
has integer roots. What is the smallest value of b for which N(b) = 20?




