\item A man walks a certain distance and rides back in $3\frac{3}{4}$ hours; he could ride both ways in $2\frac{1}{2}$ hours. How many hours would it take him to walk both ways?

\item How many line segments have both their endpoints located at the vertices of a given cube?

\item Let E(n) denote the sum of the even digits of n. For example, E(123) = 2 + 4 = 6. What is the value of 
\begin{align*}
E(1) + E(2) + E(3) +..... + E(100)
\end{align*}

\item How many two-digit positive integers N have the property that the sum of N and the number obtained by reversing the order of the digits of N is perfect square?

\item A $2 \times 3$ rectangle $3 \times 4$ rectangle are contained within a square without overlapping at any interior point, and the sides of the square are parallel to the sides of the two given rectangles. What is the smallest possible area of the square?

\item What is the greatest possible perimeter of a right-angled triangle with interger side lengths if one of the sides has length?

\item Let n be the largest integer that is the product of exactly 3 distint prime numbers, x, y and 10x + y, where x and y are digits. What is the sum of the digits of n?

\item At a party, each man danced with exactly four women and each woman danced with exactly three men. Nine men attended the party. How many woman attended the party?

\item A subset B of the set of first 100 integers had the property that no two elements of B sum to 125. What is the maximum possible number of elements in B?

\item The digits of a positive integer n are four consecutive integers in decreasing order when read from left to right. What is the sum of the possible remainders when n is divided by 37?






