\item A book is published in three volumes, the pages being numbered from 1 onwards. The page numbers are continued from the first volume of to the second volume to the third. The number of pages in the second volume is 50 more than that in the first column, and the number pages in the third volume is one and a half times that in the second. The sum of the page numbers on the first pages of the three volumes is 1709. If n is the last page number, what is the largest prime factor of n?

\item Consider all 6-digit numbers of the form $abccba$ where $b$ is odd. Determine the number of all such 6-digit numbers that are divisible by 7.

\item A point P in the interior of a regular hexagon is at distances 8, 8, 16 units from three consecutive vertices of the haxagon respectively. If r is radius of the circumscribed circle of the hexagon, what is the integer closest to r?

\item There are several tea cups in the kitchen, some with handles and the others without handles. The number of ways of selecting two cups without a handle and three with a handle is exactly 1200. What is the maximum possible number of cups in the kitchen?

\item Determine the number of 8-tuples $(\epsilon_1, \epsilon_2,.......\epsilon_8)$ such that $\epsilon_1, \epsilon_2,.........\epsilon_8 \in \{1, -1\}$ and
\begin{align*}
\epsilon_1 + 2\epsilon_2 + 3\epsilon_3 +.........8\epsilon_8
\end{align*}
is a multiple of 3.

\item Let
\begin{align*}
N = 6 + 66 + 666 +.......666....66
\end{align*}
where there are hundred $6's$ in the last term in the sum. How many times does the digit 7 occur in the number N?

\item A positive integer k is said to be good if there exists a partition of $\{1, 2, 3,......20\}$ in to disjoint proper subsets such that the sum of the numbers in each subset o the partition is k. How many good numbers are there?

\item If N is the number triangles of different shapes(i.e., not similar) whose angles are all integers(in degrees), what is $N/100$?

\item Let T be the smallest positive integer which, when divided by 11, 13, 15 leaves remainders in the sets 
$\{7, 8, 9\}$, $\{1, 2, 3\}$, $\{4, 5, 6\}$ respectively. What is the sum of the squares of the digits of T?

\item What is the number of ways in which one can choose 60 unit squares from $11 \times 11$ chessboard such that no two choosen squares have a side in common?

\item What is the number of ways in which one can colour the squares of a $4 \times 4$ chessboard with colours red and blue such that each row as well as each column has exactly two red squares and two blue squares?

\item Let N be the number of ways of distributing 8 chocolates of different brands among 3 children such that each child gets at least one chocolate, and no two children get the same number of chocolates. Find the sum of the digits of N?
