\item From a square with sides of lengths 5, triangular pieces from the four corners are removed to form a regular octagon. Find the area removed to the nearest integer?

\item Let $x_1$ be a positive real number and for every integer $n \geq 1$ let 
\begin{align*}
x_{n + 1} = 1 + x_1x_2......x_{n - 1}x_n
\end{align*}
If $x_5 = 43$, what is the sum of digits of the largest prime factor of $x_6$?

\item An ant leaves the anthill for its morning exercise. It walks 4 feet and then makes a $160^{o}$ turn to the right and walks 4 more feet. It makes another $160^{o}$ turn to the right and walks 4 more feet. If the ant continues this pattern until it reaches the anthill again. What is the distance in feet it would have walked?

\item Five persons wearing badges with numbers 1, 2, 3, 4, 5 are seated on 5 chairs around a circular table. In how many ways can they be seated so that no two persons whose badges have consecutive numbers are seated next to each other?
( Two arrangements obtained by rotation around the table are considered different.)

\item On a clock, there are two instants between 12 noon and 1 PM. when the hour hand and the minute hand are at right angles. The difference in minutes between these two instants is written as $a + \frac{b}{c}$, where a, b, c are positive integers, with $b < c$ and $b/c$ in the reduced form. What is the value of a + b + c?

\item Each of the numbers 
\begin{align*}
x_1, x_2,......,x_{101}
\end{align*}
is $\pm 1$. What is the smallest positive value of 
\begin{align*}
\sum_{1 \leq i < j \leq 101}  x_ix_j
\end{align*}

\item Find the smallest positive integer $n \geq 10$ such that n + 6 is a prime and 9n + 7 is a perfect square.

\item A pen costs $13/-$ and a note book costs $17/-$. A school spends exactly $10000/-$ in the year 2017-18 to buy x pens and y note books such that x and y are as close as possible (i.e., $|x - y|$ is minimum). Next year, in 2018-19, the school spends a little more than $10000/-$ and buys y pens and x note books. How much more did the school pay?

\item How many ordered pairs (a, b) of positive integers with $a < b$ and $100 \leq a, b \leq 1000$ satisfy 
\begin{align*}
gcd(a, b):lcm(a, b) = 1 : 495
\end{align*}

\item Consider the set $E = \{5, 6, 7, 8, 9\}$. For any partition $\{A, B\}$ of E, with both A and B non-empty, consider the number obtained by adding the product of elements of A to the product of elements of B. Let N be the largest prime number among these numbers. Find the sum of the digits of N.

\item Consider the set E of all natural numbers n such that when divided by 11, 12, 13, respectively, the remainders, in that order, are distinct prime numbers in an arithmetic progression. If N is the largest number in E, find the sum of digits of N.

\item What is the greatest integer not exceeding the sum 
\begin{align*}
\sum_{n = 1}^{1599} \frac{1}{\sqrt{n}}
\end{align*}

\item A $1 \times n$ rectangle $(n \geq 1)$ is divided into n unit $1 \times 1$ squares. Each square of this rectangle is coloured red, blue or green. Let f(n) be the number of colourings of the rectangle in which there are an even number of red squares. What is the largest prime factor of $\frac{f(9)}{f(3)}$?(The number of red squares can be zero.)

\item A village has a circular wall around it, and the wall has four gates pointing north, south, east and west. A tree stands outside the village, 16m north of the north gate, and it can be just seen appearing on the horizon from a point 48m east of the south gate. What is the diameter in meters, of the wall that surroundings the village?

\item We will say that a rearrangement of the letters of a word has no fixed letters if, when the rearrangement is placed directly below the word, no column has the same letter repeated. For instance, $H B R A T A$ is a rearrangement with no fixed of $B H A R A T$. How man distinguishable rearrangements with no fixed letters does $B H A R A T$ have?(The two $A's$ are considered identical.)

\item Let E denote the set of all natural numbers n such that $3 < n < 100$ and the set $\{1, 2, 3,......,n\}$ can be partitioned in to 3 subsets with equal sums. Find the number of elements of E?












