\begin{enumerate}[1.]
\item Find the equations of the tangents to the curves $y=x^3-x$ and $x^2-3x+2$ at their point of intersection, and the angle at which the
curves cut.
\item Prove that the line $3y=9x-16$ is a tangent to the curve $3y=x^3-3x$, and find the coordinates of the 
point of contact.
\item Prove that the tangents to the curve $y=x^3-6x^2+13x-6$ at the points $\brak{1,2}$ and $\brak{3,6}$ are parallel, and that
the tangent at the point $\brak{2,4}$ is inclined to them at an angle $\tan^{-1}\frac{3}{5}$.
\item Prove that the line $y=5x$ is a tangent to the curve
\begin{align*}
y=x^3-2x^2+x+8
\end{align*}
and find the coordinates of the point of contact.  In what other point does the line $y=5x$ meet the curve?
\item Find the equation of the tangent to the curve $y=3x^2-2x-1$ at the point $\brak{2,7}$.  Also find the coordinates of the point on the curve the tangent
at which is perpendicular to the tangent at $\brak{2,7}$.
\item Find the equation of the normal to the curve $y=2x^2-3x-5$ at the point $\brak{2,-3}$ , and find the length of the subnormal at this point.
\item Find the equation of the tangent to the curve
\begin{align*}
3y=x^3-6x^2-12x+1
\end{align*}
at the point $\brak{-1,2}$, and find the coordinates of another poin on the curve where the tangent
is parallel to that at $\brak{-1,2}$.
\item Prove that at every point of the curve $y=x^3-3x^2+3x+7$ the gradient is positive.  Table the values of $y$ and $\frac{dy}{dx}$ at the points
$x=-1,0,1,2,3$ and make a rought drawing of the curve.
\item Find the equation of the tangent and normal to the curve $y=\brak{x-1}^4$ at the point $\brak{2,1}$.  Find the area of the triangle
which the tangent and normal make with the $x$-axis.
\item Show that the curve $y=1-2x+x^3$ cuts the $x$-axis in three real points.  Find the gradient of the curve
at the point $\brak{1,0}$; also find the points at which the gradient vanishes and make a rough drawing of 
the curve.
\item Find the gradients of the curve $y=\brak{x-1}^2\brak{x-2}$ at the points where it crosses the axes.  Find also the points
at which the gradient vanishes and make a rough drawing of the curve.
\item Find the points on the curve $y=x^3-x^2+1$ at which the gradient is unity.  Find the equations of the tangents
and normals at these points.
\item Find the points in which the curve $y=1+2x-3x^2$ cuts the coordinate axes and find the gradients of the curve
at these points.  At what point does the gradient vanish?  Make a rough drawing of the
curve.
\item Show that the curve $y=\brak{x^2-1}^2$ is symmetrical about the $y$-axis.  Find its gradient and the points at which
the gradient vanishes.  In what points does the line $y=9$ cut the curve?  Make a rough drawing of the curve.
\item Show that the curve $y=x^4-4x^2$ is symmetrical about the $y$-axis.  Find the gradients of the curve
at its intersections with the $x$-axis.  find also the points where the gradient vanishes and make a
rough drawing of the curve.

\item Show that the curve $y=x^4-4x^2$ is symmetrical about the $y$-axis.  Find the gradients of the curve at its intersections
with the $x$-axis.  Find also the points where the gradient vanishes and make a rough drawing of the curve.
\item Find the gradient of the curve $y=x^2-3x-4$, and the point on the curve at which the gradient vanishes.  Also find
the gradient at the points where the curve crosses the $x$-axis and make a rough drawing of the curve.  To what
point on the $x$-axis must the origin be moved so that the curve may become symmetrical
about the $y$-axis, and what will be the equation of the curve when the position of the origin
is so changed?
\item Show that the curve whose equation is $27y=x^3-27x$ is symmetrical in opposite quadrants.  Prove that
the tangent to the curve at the origin is $x+y=0$.  Find the gradient at the other intersections with the $x$-axis.  Also
find at what points the tangent is parallel to the $x$-axis, and make a rough drawing of the curve.
\item Find the equation of the locus of a point which moves so that its distance from the point $\brak{2,1}$
is twice its distance from the line $3x+4y=2$.
\item Find the locus of a point which moves so that its distance from the origin is half the  distance from the
line $3x+4y=2$.
\item A point $P$ moves so that $PA^2+PB^2=AB^2$, where $A$, $B$ are the points $\brak{2,0}$, $\brak{0,3}$.  Find the equation of the locus of $P$.
\item Find the locus of a point whose distance from the point $A\brak{3,0}$ is three times its distance from the point $B \brak{-1,0}$.
Prove that the tangents to the locus at the points $\brak{0,0}$ and $\brak{-3,0}$ are parallel to the $y$-axis.
\item The coordiantes of a point are given in terms of a variable parameter $t$ by the relations $x=\frac{t}{t+1}, y = \frac{t}{t-1}$.  Find the equation of the locus
of the point, and prove that the equation of the tangent at any point $t$
on the locus is $\brak{t+1}^2x+\brak{t-1}^2y=2t^2$.
\item The coordinates of a point are given by the relations $x = t + \frac{1}{t}$, $y = t - \frac{1}{t}$ and $t$ is a variable parameter.  Find the
equation of the locus of the point for different values of $t$, and also the equations of the
tangent at the point denoted by $t$.
\end{enumerate}
