\begin{enumerate}[1.]
\item Mark on a diagram the points $\brak{-2,4}, \brak{3,-5}$ and find the distance between them.

%
\item
Find the lengths of the lines joining the following pairs of points:
\begin{enumerate}
\item $\brak{-1,1}$ and $\brak{2,-1}$;
\item $\brak{4,3}$ and $\brak{-2,2}$;
\item \brak{a,b} and $\brak{-b,a}$.
\end{enumerate}

\item Prove that the line joining the points $\brak{2,1}$ and $\brak{4,7}$ has the same middle point as the line joining $\brak{5,4}$ and $\brak{1,4}$,
and hence that the four points are the corners of a parallelogram.
\item Prove that the points $\brak{-3,-4}, \brak{2,6}$ and $\brak{-6,10}$  are at the corners of a right-angled
traingle.
\item Plot the points $\brak{0,2},\brak{1,1},\brak{4,4}\text{ and }\brak{3,5}$ and prove that they are at the corners of a rectangle.
\item Plot the points $\brak{-2,-2},\brak{-1,2},\text{ and }\brak{3,1}$ and prove that they are at the corners of an isosceles triangle.
\item In the last question, find the distance of the vertex of the triangle from the middle point of the base.
\item Prove that the points $\brak{-1,0}$, $\brak{0,3}$, $\brak{3,2}$ and $\brak{2,-1}$ are at the corners of a square.
\item Prove that the points $\brak{-1,0}$, $\brak{3,1}$, $\brak{2,2}$  and $\brak{-2,1}$ are at the corners of a parallelogram. By finding
the coordinates verify that the joins of the middle points of pairs of opposite sides have the same middle point.
\item Prove that the points $\brak{21,-2}$, $\brak{15,10}$, $\brak{-5,0}$  and $\brak{1,-12}$ are at the corners of a rectangle, and find the
coordinates of its centre.
\item Find the lengths of the medians of the triangle whose corners are at the points $\brak{1,2}$, $\brak{0,3}$ and $\brak{-1,-2}$.
\item Find the coordinates of the points that divide the line joining the points $\brak{-35,-20}$ and $\brak{5,-10}$ into four equal parts.
\item Find the coordinates of the points of trisection of the line joining the points $\brak{-5,5}$ and $\brak{25,10}$.
\item Prove that the middle point of the line joining the points $\brak{-5,12}$ and $\brak{9,-2}$ is a point of trisection of the line
joining the points $\brak{-8,-5}$ and $\brak{7,10}$.
\item The points $\brak{8,5}$, $\brak{-7,-5}$ and $\brak{-5,5}$ are three of the corners of a parallelogram.  Find the coordinates of
the remaining corner which is to be taken as opposite to $\brak{-7,-5}$.
\item The point $\brak{2,6}$ is the intesection of the diagonals of a parallelogram two of whose corners are at the points $\brak{7,16}$ and $\brak{10,2}$.
Find the coordinates of the remaining corners.
\item Find the area of the triangle whose corners are the points $\brak{2,3}$, $\brak{-4,7}$ and $\brak{5,-2}$.  
\item Find the coordinates of  points which divide the join of $\brak{2,3}$, $\brak{-4,5}$ externally in the ratio $2:3$, and also
externally in the ratio $3:2$.
\item Prove that if $\brak{x_1,y_1},\brak{x_2,y_2}$ and $\brak{x_3,y_3}$ are the corners of a triangle the coordinates of its centroid are
\begin{equation*}
\frac{1}{2}\brak{x_1+x_2+x_3}, \frac{1}{2}\brak{y_1+y_2+y_3.}
\end{equation*}
\end{enumerate}
%\bibliography{IEEEabrv,gvv_opt}

%\input{./chapters/chapter2} 
%%
%\newpage
%\section{$M$-ary Modulation}
%\input{./chapters/chapter3} 
%
%\newpage
%\section{BER in Rayleigh Flat Slowly Fading Channels}
	%\input{./chapters/chapter4} 




