\renewcommand{\theequation}{\theenumi}
\begin{enumerate}[label=\arabic*.,ref=\thesubsection.\theenumi]
\numberwithin{equation}{enumi}
%
\item A traffic signal board, indicating ‘SCHOOL AHEAD’, is an equilateral triangle with side 'a'. Find the area of the signal board, using Heron's formula. If its perimeter is 180 cm, what will be the area of the signal board?
\item The triangular side walls of a flyover have been used for advertisements. The sides of the walls are 122 m, 22 m and 120 m. The advertisements yield an earning of \rupee 5000 per $m^2$ per year.  A company hired one o its walls for 3 months. How  much rent did it pay?
\item There is a slide in a park. One of its side walls has been painted in some colour with a message ``KEEP THE PARK GREEN AND CLEAN". If the sides of the wall are 15 m, 11 m and 6 m, find the area painted in colour.
\item Find the area of a triangle two sides of which are 18cm and 10cm and the perimeter is 42cm.
\item Sides of a triangle are in the ratio of 12 : 17 : 25 and its perimeter is 540cm. Find its area. 
\item  An isosceles triangle has perimeter 30 cm and each of the equal sides is 12 cm. Find the area of the triangle.
%
\item In quadrilateral $ACBD, AC = AD$ and $AB$ bisects $\angle  A$ (see Fig. 7.16). Show that $\triangle  ABC \cong \triangle  ABD$. What can you say about $BC$ and $BD$?
%
\item $ABCD$ is a quadrilateral in which $AD = BC$ and $\angle  DAB = \angle  CBA$ . Prove that
\begin{enumerate}
\item  $\triangle  ABD \cong  \triangle  BAC $
\item $ BD = AC $
\item  $\angle  ABD = \angle  BAC$.
\end{enumerate}
%
\item $l$ and $m$ are two parallel lines intersected by another pair of parallel lines p and q 
to form the quadrilateral $ABCD$. Show that $\triangle  ABC \cong  \triangle  CDA$.
%
\item Line $l$ is the bisector of $ \angle  A$ and $B$ is any point on $l$. $BP$ and $BQ$ are perpendiculars from $B$ to the arms of $\angle  A$ (see Fig. 7.20). Show that: 
\begin{enumerate}
\item  $\triangle  APB \cong  \triangle  AQB$ 
\item  $BP = BQ$ or $B$ is equidistant from the arms of $\angle  A$.
\end{enumerate}
%
\item $ABCE$ is a quadrilateral and $D$ is a point on $BC$ such that, $AC = AE, AB = AD$ and $\angle  BAD = \angle  EAC$. Show that $BC = DE$.
%
\item In right triangle $ABC$, right angled at $C, M$ is the mid-point of hypotenuse $AB$. $C$ is joined to $M$ and produced to a point $D$ such that $DM = CM$. Point $D$ is joined to point $B$.
Show that: 
\begin{enumerate}
\item $ \triangle  AMC \cong  \triangle  BMD $
\item $\angle  DBC$ is a right angle. 
\item $\triangle  DBC \cong  \triangle  ACB$
\item $ CM = \frac{1}{ 2} AB$
\end{enumerate}
%
\item In an isosceles $\triangle ABC$, with $AB = AC$, the bisectors of $\angle B$ and $\angle C$ intersect each other at $O$. Join $A$ to $O$. Show that :
\begin{enumerate} 
\item $OB = OC$ 
\item $AO$ bisects $\angle A$
\end{enumerate}
\item In $\triangle ABC$, $AD$ is the perpendicular bisector of $BC$. Show that $\triangle ABC$ is an isosceles triangle in which $AB = AC$.
\item $ABC$ is an isosceles triangle in which altitudes $BE$ and $CF$ are drawn to equal sides $AC$ and $AB$ respectively . Show that these altitudes are equal.
%
\item $ABC$ is a triangle in which altitudes $BE$ and $CF$ to sides $AC$ and $AB$ are equal. Show that
%
\begin{enumerate} 
\item $\triangle  ABE \cong  \triangle  ACF $
\item  $AB = AC$, i.e., $ABC$ is an isosceles triangle.
\end{enumerate}
%
\item $ABC$ and $DBC$ are two isosceles triangles on the same base $BC$. Show that $\angle ABD = \angle ACD$.
%
\item  $\triangle  ABC$ and $\triangle  DBC$ are two isosceles triangles on the same base $BC$ and vertices $A$ and $D$ are on the same side of $BC$. If $AD$ is extended to intersect $BC$ at $P$, show that
\begin{enumerate}
\item $\triangle  ABD \cong  \triangle  ACD $
\item $\triangle  ABP \cong  \triangle  ACP $
\item $AP$ bisects $\angle  A$ as well as $\angle  D$. 
\item $AP$ is the perpendicular bisector of $BC$.
\end{enumerate}
\item $AD$ is an altitude of an isosceles $\triangle ABC$ in which $AB = AC$. Show that 
\begin{enumerate}
\item $AD$ bisects $BC$
\item $AD$ bisects $\angle  A$. 
\end{enumerate}

\item  Two sides $AB$ and $BC$ and median $AM$ of one triangle $ABC$ are respectively equal to sides $PQ$ and $QR$ and median $PN$ of $\triangle  PQR$. Show that: 
\begin{enumerate}
\item $\triangle  ABM \cong  \triangle  PQN $
\item $\triangle  ABC \cong  \triangle  PQR$
\end{enumerate}
\item  $BE$ and $CF$ are two equal altitudes of a triangle $ABC$. Using RHS congruence rule, prove that the triangle $ABC$ is isosceles.
\item  $ABC$ is an isosceles triangle with $AB = AC$. Draw $AP \perp BC$ to show that $\angle  B = \angle  C$.
%
\item $\triangle ABC$ is an isosceles triangle in which $AB = AC$. Side $BA$ is produced to $D$ such that $AD = AB$. Show that $\angle BCD$ is a right angle.
%
\item $ABC$ is a right angled triangle in which $\angle A$ = 90$\degree$ and $AB = AC$. Find $\angle B$ and $\angle C$.
%
\item Show that in a right angled triangle, the hypotenuse is the longest side.
\item Sides AB and AC of $\triangle  ABC$ are extended to points P and Q respectively. Also, $\angle  PBC < \angle  QCB$. Show that $AC > AB$.

\item Line segments $AD$ and $BC$ intersect at $O$ and form $\triangle OAB$ and $\triangle ODC$. $\angle  B < \angle  A$ and $\angle  C < \angle  D$. Show that $AD < BC$.

\item $AB$ and $CD$ are respectively the smallest and longest sides of a quadrilateral $ABCD$. Show that $\angle  A > \angle  C$ and $\angle  B > \angle  D$.
%
\item In $\triangle PQR,  PR > PQ$ and $PS$ bisects $\angle  QPR$. Prove that $\angle  PSR > \angle  PSQ$.
%
\item Show that of all line segments drawn from a given point not on it, the perpendicular line segment is the shortest.
%
\item $ABC$ is a triangle. Locate a point in the interior of $\triangle  ABC$ which is equidistant from all the vertices of $\triangle  ABC$.
\item  In a triangle locate a point in its interior which is equidistant from all the sides of the triangle.
%
\item Draw the graphs of the equations 
\begin{align}
\myvec{1 & -1}\vec{x} + 1 &= 0 
\\
\myvec{ 3 & 2} - 12 &= 0
\end{align}
%
 Determine the coordinates of the vertices of the triangle formed by these lines and the x-axis, and shade the triangular region.
%
\item In a $\triangle ABC, \angle C = 3 \angle B = 2 (\angle A + \angle B)$. Find the three angles. 
\item Draw the graphs of the equations $5x – y = 5$ and $3x – y = 3$. Determine the co-ordinates of the vertices of the triangle formed by these lines and the y axis.

\item The vertices of $\triangle PQR$ are 

$
\vec{P} = \myvec{2 \\1},
\vec{Q} = \myvec{-2\\3},
\vec{R} = \myvec{4\\5}.
$
Find the equation of the median through the vertex $\vec{R}$.
\item In the $\triangle ABC$ with vertices
$
\vec{A}=\myvec{2\\3}, 
\vec{B}=\myvec{4\\-1},
 \vec{C}=\myvec{1\\2}
$,
find the equation and length of the altitude from the vertex $\vec{A}$.
\item Find the area of the triangle whose vertices are
\begin{enumerate}
\item \myvec{2\\3}, \myvec{-1\\0},  \myvec{2\\-4}
\item  \myvec{-5\\-1},  \myvec{3\\-5},  \myvec{5\\2}
\end{enumerate}
\item Find the area of the triangle formed by joining the mid points o the sides of a triangle whose vertices are  \myvec{0\\-1},  \myvec{2\\1},  \myvec{0\\3}.
\item Verify that the median of $\triangle ABC$ with vertices $\vec{A}=\myvec{4\\-6},  \vec{B}=\myvec{3\\-2}$ and  $\vec{C} =  \myvec{5\\2}$ divides it into two triangles of equal areas.
\item The vertices of $\triangle ABC$ are $\vec{A}=\myvec{4\\6},  \vec{B}=\myvec{1\\5}$ and  $\vec{C} =  \myvec{7\\2}$.  A line is drawn to intersect sides $AB$ and $AC$ at $D$ and $E$ respectively, such that
\begin{align}
\frac{AD}{AB}=\frac{AE}{AC}= \frac{1}{4}
\end{align}
%
Find 
\begin{align}
\frac{\text{area of }\triangle ADE}{\text{area of }\triangle ABC}.
\end{align}
\item Let $\vec{A}=\myvec{4\\2},  \vec{B}=\myvec{6\\5}$ and  $\vec{C} =  \myvec{1\\4}$ be the vertices of $\triangle ABC$.
\begin{enumerate}
\item The median from $\vec{A}$ meets $BC$ at $\vec{D}$.  Find the coordinates of the point $\vec{D}$.
\item Find the coordinates of the point $\vec{P}$ on $AD$ such that $AP:PD = 2:1$.
\item Find the coordinates of the points $\vec{Q}$ and $\vec{R}$ on medians $BE$ and $CF$ respectively such that $BQ:QE = 2:1$ and $CR:RF = 2:1$.
\end{enumerate}
\item In $\triangle ABC$, Show that the centroid 
\begin{align}
\vec{O} = \frac{\vec{A}+\vec{B}+\vec{C}}{3}
\end{align}
\item Show that the points 
\begin{align}
\vec{A} = \myvec{2\\-1 \\1},
\vec{B} = \myvec{1\\-3 \\-5},
\vec{C} = \myvec{3\\ -4\\-4}
\end{align}
%
are the vertices of a right angled triangle.
\item In $\triangle ABC$, 
$
\vec{A} = \myvec{1\\2 \\3},
\vec{B} = \myvec{-1\\0 \\0},
\vec{C} = \myvec{0\\ 1\\2}.
$
Find $\angle B$.
\item Show that the vectors 
$
\myvec{2\\-1 \\1},
\myvec{1\\-3 \\-5},
\myvec{3\\ -4\\-4}
$
form the vertices of a right angled triangle.
\item Find the area of a triangle having the points 
$
\vec{A} = \myvec{1\\1 \\1},
\vec{B} = \myvec{1\\2 \\3}, \text{ and }
\vec{C} = \myvec{2\\ 3\\1}
$
as its vertices.
\item Find the area of a triangle with vertices
$
\vec{A} = \myvec{1\\1 \\2},
\vec{B} = \myvec{2\\3 \\5}, \text{ and }
\vec{C} = \myvec{1\\ 5\\5}
$
\item A girl walks 4km west, then she walks 3km in a direction $30\degree$ east of north and stops.  Determine the girl's displacement from her initial point of departure.
\item Find the direction vectors of the sides of a triangle with vertices
$
\vec{A} = \myvec{3\\5 \\-4},
\vec{B} = \myvec{-1\\1 \\2}, \text{ and }
\vec{C} = \myvec{-5\\ -5\\-2}
$
\item Without using the Pythagoras theorem, show that the points \myvec{4\\ 4}, \myvec{3\\ 5} and \myvec{–1\\ –1} are the vertices of a right angled triangle.
\item Check whether 
\begin{align}
\myvec{5\\-2}, \myvec{6\\4}, \myvec{7\\-2}
\end{align}
are the vertices of an isosceles triangle.
%
\item A circus artist is climbing a 20m long rope, which is tightly stretched and tied from the top of a vertical pole to the ground.  Find the height of the pole, if the angle made by the rope with the ground level is 30$\degree$.
%
\item A tree breaks due to storm and the broken part bends so that the top of the tree touches the ground making an angle of 30$\degree$ with it.  The distance between the foot of the tree to the point where the top touches the ground is 8m.  Find the height of the tree.
%
\item A contractor plans to install two slides for the children to play in a park.  For the children below the age of 5 years, she prefers to have a slide whose top is at a height of 1.5m, and is inclined at an angle of 30$\degree$  to the ground, whereas for elder children she wants to have a steep slide at a height of 3m, and inclined at an angle of 60$\degree$ to the ground.  What should be the length of the slide in each case?
%
\item The angle of elevation of the top of a tower from a point on the ground, which is 30m away from the foot of the tower, is 30$\degree$.  Find the height of the tower.
%
\item A kite is flying at a height of 60m above the ground.  The string attached to the kite is temporarily tied to a point on the ground.  The inclination of the string with the ground is $60\degree$.  Find the length of the string, assuming that there is no slack in the string.
%
\item A 1.5m tall boy is standing at some distance from a 30m tall building.  The angle of elevation from his eyes to the top of the building increases from 30$\degree$
 to 60$\degree $ as he walks towards the building.  Find the distance he walked towards the building.

\item From a point on the ground, the angles of elevation of the bottom and the top of a transmission tower fixed at the top of a 20 m high building are 45$\degree$ and 60$\degree$ respectively. Find the height of the tower.

\item A statue, 1.6 m tall, stands on the top of a pedestal. From a point on the ground, the angle of elevation of the top of the statue is 60$\degree$ and from the same point the angle of elevation of the top of the pedestal is 45$\degree$. Find the height of the pedestal.
\item The angle of elevation of the top of a building from the foot of the tower is 30$\degree$ and the angle of elevation of the top of the tower from the foot of the building is 60$\degree$. If the tower is 50 m high, find the height of the building.
\item Two poles of equal heights are standing opposite each other on either side of the road, which is 80 m wide. From a point between them on the road, the angles of elevation of the top of the poles are 60$\degree$ and 30$\degree$, respectively. Find the height of the poles and the distances of the point from the poles.
\item A TV tower stands vertically on a bank of a canal. From a point on the other bank directly opposite the tower, the angle of elevation of the top of the tower is 60$\degree$. From another point 20 m away from this point on the line joing this point to the foot of the tower, the angle of elevation of the top of the tower is 30$\degree$. Find the height of the tower and the width of the canal.
\item From the top of a 7 m high building, the angle of elevation of the top of a cable tower is 60$\degree$ and the angle of depression of its foot is 45$\degree$. Determine the height of the tower.
\item As observed from the top of a 75 m high lighthouse from the sea-level, the angles of depression of two ships are 30$\degree$ and 45$\degree$. If one ship is exactly behind the other on the same side of the lighthouse, find the distance between the two ships.
\item A 1.2 m tall girl spots a balloon moving with the wind in a horizontal line at a height of 88.2 m from the ground. The angle of elevation of the balloon from the eyes of the girl at any instant is 60$\degree$. After some time, the angle of elevation reduces to 30$\degree$. Find the distance travelled by the balloon during the interval.
\item A straight highway leads to the foot of a tower. A man standing at the top of the tower observes a car at an angle of depression of 30$\degree$, which is approaching the foot of the tower with a uniform speed. Six seconds later, the angle of depression of the car is found to be 60$\degree$. Find the time taken by the car to reach the foot of the tower from this point.
\item The angles of elevation of the top of a tower from two points at a distance of 4 m and 9 m from the base of the tower and in the same straight line with it are complementary. Prove that the height of the tower is 6 m.

\end{enumerate}
%

