\begin{enumerate}[1.]
\item Find the locus of a point which is equidistant from the points $\brak{6,-3}$, $\brak{-4,7}$.
\item Find the point on the line
\begin{align*}
2x+5y+7=0
\end{align*}
which is equidistant from the points $\brak{2,-3}$, $\brak{-4,1}$.
\item Find the coordinates of the circumcentre of the triangle whose corners are at the points $\brak{4,3}$, $\brak{-1,2}$, $\brak{2,-2}$.
\item Find the equations of the lines through $\brak{3,1}$ which are respectively parallel and perpendicular to the line joining the points $\brak{2,4}$, $\brak{5,-6}$.
\item Find the locus of a point at which the join of the points $\brak{2,1}$ and $\brak{-3,4}$ subtends a right angle.
\item Find the orthocentre of a triangle whose corners are at the points $\brak{1,2}$, $\brak{-3,-4}$, $\brak{6,2}$.
\item Prove that the line joining the points $\brak{2,-1}$, $\brak{-3,5}$ makes with the axes a triangle of area $\frac{49}{60}$.
\item $ABCD$ is a parallelogram and the coordinates of $A$, $B$ and $C$ are $\brak{2,4}$, $\brak{1,2}$ and $\brak{4,1}$ Find the coordinates of $D$.
\item Find the area of the triangle formed by the lines 
\begin{align*}
3x-2y=5, 3y+4x=7, y +2 = 0
\end{align*}
\item Find the cetre of the inscribed circle of the triangle whose sides are
\begin{align*}
3x-4y=0, 12-5y=0, 4x+3y=8
\end{align*}
\item The ends of a diagonal of a sqaure are on the coordinate axes at the points $\brak{2a,0}$, $\brak{0,a}$.  Find the equations of the sides.
\item The sides of a triangle $ABC$ are
\begin{align*}
AB=3, BC = 5, CA = 4
\end{align*}
and $A, B$ are on the axes $OX$, $Oy$ respectively, while $AC$ makes an angle $\theta$ with $OX$.  Prove that the locus of $C$, as $\theta$ varies, is given by the equation
\begin{align*}
16x^2-24xy+25y^2 = 256
\end{align*}
\item Prove that the locus of a point at which the join of the points $\brak{a,0}$ and $\brak{-a,0}$ subtends an angle of $45\degree$ is
\begin{align*}
x^2+y^2-2ay = a^2
\end{align*}
\item Prove that the line
\begin{align*}
ax+by+c=0
\end{align*}
divides the join of the points $\brak{x_1,y_1}$, $\brak{x_2,y_2}$ in the ratio
\begin{align*}
-\frac{ax_1+by_1+c}{ax_2+by_2+c}
\end{align*}
\item Find the equation of the line joining the point $\brak{x_1,y_1}$, to the point of intersection of the lines
\begin{align*}
ax+by+c = 0, a_1x+b_1y+c_1 = 0
\end{align*}
\item Prove that the equations of the diagonals of the parallelogram whose sides are
\begin{align*}
ax+by+c = 0, ax+by+d = 0
\\
a_1x+b_1y+c_1 = 0, a_1x+b_1y+d_1 = 0
\end{align*}
are
{\small
\begin{align*}
\brak{c_1-d_1}\brak{ax+by+c}-\brak{c-d}\brak{a_1x+b_1y+c_1} = 0
\\
\brak{c_1-d_1}\brak{ax+by+c}+\brak{c-d}\brak{a_1x+b_1y+c_1} = 0
\\
\brak{c-d}\brak{c_1-d_1}/\brak{ab_1-a_1b}.
\end{align*}
}
\item Prove that for all values of $k$ the line
\begin{align*}
\brak{2+k}x+\brak{1-2k}y + 5 = 0
\end{align*}
passes through a fixed point, and find its coordinates.
\item Find the angle between the lines
\begin{align*}
x^2 - 2xy \sec \theta + y^2 = 0
\end{align*}
\item Prove that the pairs of straight lines represented by
\begin{align*}
x^2+xy = 0, 6x^2-xy-y^2 = 0
\end{align*}
are such that the angles between one pair are equal to the angles between the other pair.
\item Find the angles between the lines
\begin{align*}
x^3-3x^2y-3xy^2+y^3 = 0
\end{align*}
\item Find the area of the triangle whose sides are given by
\begin{align*}
x^2+3y^2 = 4xy \text{ and } 3x+4y=7
\end{align*}
\item Show that the equation
\begin{align*}
6x^2-xy-15y^2-11x+31y-10=0
\end{align*}
represents two straight lines, and find the equations of the bisectors of the angles between them.
\item For what value of $k$ does the equation
\begin{align*}
12x^2+7xy+ky^2+13x-y+3 = 0
\end{align*}
represent two straight lines? What is the angle between them?
\item For what values of $k$ does the equation
\begin{align*}
6x^2+kxy-3y^2+4x+5y-2 = 0
\end{align*}
represent two straight lines?
\end{enumerate}