\renewcommand{\theequation}{\theenumi}
\begin{enumerate}[label=\arabic*.,ref=\thesubsection.\theenumi]
\numberwithin{equation}{enumi}
\item If P(A)=$\frac{7}{13}, P(B)=\frac{9}{13}$ and $P(A\cap B)=\frac{4}{13},$ Evaluate P(A/B)?\\

\item A family has two children. What is the probability that both the children are boys given that at least one of them is a boy?\\

\item Ten cards numbered 1 to 10 are placed in a box, mixed up thoroughly and then one card is drawn randomly. If it is known that the number on the drawn card is more than 3, what is the probability that it is an even number?\\

\item In a school, there are 1000 students, out of which 430 are girls. It is known that out of 430,  10 percentage of the girls study in class XII. What is the probability that a student chosen randomly studies in Class XII given that the chosen student is a girl?\\

\item A die is thrown three times. Events A and B are defined as below:\\
A : 4 on the third throw.\\
B : 6 on the first and 5 on the second throw.\\
Find the probability of A given that B has already occurred?\\

\item A die is thrown twice and the sum of the numbers appearing is observed to be 6. What is the conditional probability that the number 4 has appeared at least once?\\

\item Consider the experiment of tossing a coin. If the coin shows head, toss it again but if it shows tail, then throw a die. Find the conditional probability of the event that "the die shows a number greater than 4" given that "there is at least one tail".\\

\item An urn contains 10 black and 5 white balls. Two balls are drawn from the urn one after the other without replacement. What is the probability that both drawn balls are black?\\

\item Three cards are drawn successively, without replacement from a pack of 52 well shuffled cards. What is the probability that first two cards are kings and the third card drawn is an ace?\\

\item A die is thrown. If E is the event "the number appearing is a multiple of 3" and F be the event "the number appearing is even" then find whether E and F are independent ?\\

\item An unbiased die is thrown twice. Let the event A be "odd number on the first throw" and B the event "odd number on the second throw". Check the independence of the events A and B.\\

\item Three coins are tossed simultaneously. Consider the event E "three heads or three tails", F "at least two heads" and G "at most two heads". Of the pairs (E,F), (E,G) and (F,G), which are independent? which are dependent?\\

\item Prove that if E and F are independent events, then so are the events E and $F^{'}$.\\

\item If A and B are two independent events, then the probability of occurrence of at least one of A and B is given by 1- $P(A^{'}) P(B^{'})$\\

\item A person has undertaken a construction job. The probabilities are 0.65 that there will be strike, 0.80 that the construction job will be completed on time if there is no strike, and 0.32 that the construction job will be completed on time if there is a strike. Determine the probability that the construction job will be completed on time.\\

\item Bag I contains 3 red and 4 black balls while another Bag II contains 5 red and 6 black balls. One ball is drawn at random from one of the bags and it is found to be red. Find the probability that it was drawn from Bag II.\\

\item Given three identical boxes I, II and III, each containing two coins. In box I, both coins are gold coins, in box II, both are silver coins and in the box III, there is one gold and one silver coin. A person chooses a box at random and takes out a coin. If the coin is of gold, what is the probability that the other coin in the box is also of gold?\\

\item Suppose that the reliability of a HIV test is specified as follows: Of people having HIV, 90$\%$ of the test detect the disease but 10$\%$ go undetected. Of people free of HIV, 99$\%$ of the test are judged HIV –ve but 1$\%$ are diagnosed as showing HIV +ve. From a large population of which only 0.1$\%$ have HIV, one person is selected at random, given the HIV test, and the pathologist reports him/her as HIV +ve. What is the probability that the person actually has HIV?\\

\item In a factory which manufactures bolts, machines A, B and C manufacture respectively 25$\%$, 35$\%$ and 40$\%$ of the bolts. Of their outputs, 5, 4 and 2 percent are respectively defective bolts. A bolt is drawn at random from the product and is found to be defective. What is the probability that it is manufactured by the machine B?\\

\item A doctor is to visit a patient. From the past experience, it is known that the probabilities that he will come by train, bus, scooter or by other means of transport are respectively $\frac{3}{10},\frac{1}{5},\frac{1}{10}$ and $\frac{2}{5}.$ The probabilities that he will be late are $\frac{1}{4},\frac{1}{3}$ and $\frac{1}{12},$ if he comes by train, bus and scooter respectively, but if he comes by other means of transport, then he will not be late. When he arrives, he is late. What is the probability that he comes by train?\\

\item A man is known to speak truth 3 out of 4 times. He throws a die and reports that it is a six. Find the probability that it is actually a six.\\

\item A person plays a game of tossing a coin thrice. For each head, he is given Rs 2 by the organiser of the game and for each tail, he has to give Rs 1.50 to the organiser. Let X denote the amount gained or lost by the person. Show that X is a random variable and exhibit it as a function on the sample space of the experiment.\\

\item A bag contains 2 white and 1 red balls. One ball is drawn at random and then put back in the box after noting its colour. The process is repeated again. If X denotes the number of red balls recorded in the two draws, describe X.\\

\item Two cards are drawn successively with replacement from a well shuffled deck of 52 cards. Find the probability distribution of the number of aces.\\

\item Find the probability distribution of number of doublets in three throws of a pair of dice?\\

\item Let X denote the number of hours you study during a randomly selected school day. The probability that X can take the values x, has the following form, where k is some unknown constant.\\
P(X=x)= $\begin{pmatrix} 0.1, if x= 0 \\ kx,if x= 1 or 2 \\ k(5-x), if x= 3 or 4 \\ 0, otherwise \end{pmatrix}$\\
(a) Find the value of k.\\
(b) What is the probability that you study at least two hours ? Exactly two hours? At
most two hours?\\

\item Let a pair of dice be thrown and the random variable X be the sum of the numbers that appear on the two dice. Find the mean or expectation of X.\\

\item Find the variance of the number obtained on a throw of an unbiased die.\\

\item Two cards are drawn simultaneously (or successively without replacement) from a well shuffled pack of 52 cards. Find the mean, variance and standard deviation of the number of kings.\\

\item Six balls are drawn successively from an urn containing 7 red and 9 black balls. Tell whether or not the trials of drawing balls are Bernoulli trials when after each draw the ball drawn is\\
(i) replaced \\
(ii) not replaced in the urn.\\

\item If a fair coin is tossed 10 times, find the probability of\\
(i) exactly six heads\\
(ii) at least six heads\\
(iii) at most six heads\\

\item Ten eggs are drawn successively with replacement from a lot containing 10$\%$ defective eggs. Find the probability that there is at least one defective egg.\\

\item Coloured balls are distributed in four boxes as shown in the following table:\\
\\$\begin{tabular}{||c c c c c||} 
 \hline
 Box & Black & White & Red & Blue \\
 \hline\hline
 I & 3 & 4 & 5 & 6 \\
 \hline
 II & 2 & 2 & 2 & 2 \\
 \hline
 III & 1 & 2 & 3 & 1 \\
 \hline
 IV & 4 & 3 & 1 & 5 \\
 \hline
\end{tabular}$\\
\\A box is selected at random and then a ball is randomly drawn from the selected box. The colour of the ball is black, what is the probability that ball drawn is from the box III?\\

\item Find the mean of the Binomial distribution B(4,$\frac{1}{3}$).\\

\item The probability of a shooter hitting a target is $\frac{3}{4}$. How many minimum
number of times must he/she fire so that the probability of hitting the target at least
once is more than 0.99?\\

\item A and B throw a die alternatively till one of them gets a '6' and wins the game. Find their respective probabilities of winning, if A starts first.\\

\item If a machine is correctly set up, it produces 90$\%$ acceptable items. If it is
incorrectly set up, it produces only 40$\%$ acceptable items. Past experience shows that
80$\%$ of the set ups are correctly done. If after a certain set up, the machine produces 2 acceptable items, find the probability that the machine is correctly setup.\\

    \end{enumerate}
%\end{document}
    
