\renewcommand{\theequation}{\theenumi}
\begin{enumerate}[label=\arabic*.,ref=\thesubsection.\theenumi]
\numberwithin{equation}{enumi}


\item Find the maximum and minimum values, if any, of the following functions given by 
%
\begin{enumerate}
\item $f(x) = \brak{2x-1}^2+3$
\item $f(x) = 9x^2+12x+2$
\item $f(x) = -\brak{x-1}^2+10$
\item $f(x) = x^2$.
\end{enumerate}
\item Find the absolute maximum and absoute minimum value of the following functions in the given intervals
%
\begin{enumerate}
\item $f(x) = 4x - \frac{1}{2}x^2, x \in \brak{-2,\frac{9}{2}}$
\item $f(x) = \brak{x-1}^2 + 3,  x \in \brak{-3,1}$
\end{enumerate}
%
\item Find the maximum profit that a company can make, if the profit function is given by
\begin{align}
p(x) = 41-72x - 18x^2
\end{align}
%
\item Find two positive numbers whose sum is 15 and the sum of whose squares is minimum.
\item Find two numbers whose sum is 24 and whose product is as large as possible.
\item Find two positive numbers whose sum is 16 and the sum of whose cubes is minimum.
\item The sum of the perimeter of a circle and square is $k$, where $k$ is some constant. Prove that the sum of their areas is least when the side of square is double the radius of the circle.
\item A window is in the form of a rectangle surmounted by a semicircular opening. The total perimeter of the window is 10 m. Find the dimensions of the window to admit maximum light through the whole opening.

\item Find the shortest distance of the point $\myvec{0\\c}$ from the parabola $y = x^2$, where $\frac{1}{2} \le c \le 5$.
\item Find the maximum area of an isosceles triangle inscribed in the ellipse 
%
\begin{align}
\vec{x}^T\myvec{a^2 & 0 \\ 0 & b^2}\vec{x} = a^2b^2
\end{align}
%
with its vertex at one end of the major axis.


\end{enumerate}
%\end{document}
