In the following problems, the equation of a parabola is assumed to be \eqref{eq:parab_standard}
and capital letters refer to Fig. \ref{fig:parabola} unless the contrary is stated.
\renewcommand{\theequation}{\theenumi}
\begin{enumerate}[label=\arabic*.,ref=\thesubsection.\theenumi]
\item Prove that as $\vec{P}$ moves along the curve $GP^2$ varies as $SG$.
\item Prove that, if $PP_1$ is a double ordinate and $PX$ meets the curve in $\vec{Q}$,
then $P_1Q$ passes through $\vec{S}$.
\item Prove that, if $PSP_1$ is a focal chord and $AP$, $AP_1$ meet the latus rectum in $\vec{Q}$, $\vec{Q}_1$,
the $SQ$, $SQ_1$ are equal to the ordinates of $\vec{P}_1$ and $\vec{P}$.
\item Prove that, if the tangents at $\vec{P}$, $\vec{Q}$ intersect in $\vec{T}$, then
\begin{align}
ST^2=SP.SQ.
\end{align}
\item Prove that, if the tangent at the end $\vec{Q}$ of a focal chord $PSQ$ meets the latus rectum
in $\vec{R}$, then $PGR$ is a right angle.
\item Tangents at $\vec{P}$, $\vec{Q}$, $\vec{R}$ on a parabola form a triangle $UVW$.  Show that the centroids of
the triangles $PQR$ and $UVW$ lie on the same diameter.
\item Prove that, if the difference of the ordinates of two points on a
parabola is constant, then the locus of the point of intersection of the tangents at
these points is an equal parabola.
\item Prove that, if two tangents intercept a fixed length on the tangent at the vertex, the locus
of their intersections is an equal parabola.
\item The chord of contact of tangents from any point $\vec{Q}$ meets the tangent
at the vertex in $\vec{R}$.  Prove that the tangent of the angle which $AQ$ makes with the axis
is $\frac{2a}{AR}$.
\item The parameters, $t$, $t_1$ of two points on a parabola are
connected by the relation $t=k^2t_1$, prove that the tangents at the points intersect on the
curve
\begin{align}
\vec{x}^T\myvec{0 & 0\\0 & 1}\vec{x}-\brak{k+\frac{1}{k}}^2a\myvec{1 & 0 }\vec{x}= 0 
\end{align}
\item Show that the length of the normal chord at the point of parameter $t$ is
\begin{align}
\frac{4a}{t^2}\brak{1+t^2}^{\frac{3}{2}}
\end{align}
\item Prove that the locus of intersection of tangents at the ends of a normal
chord is
\begin{align}
\brak{x+2a}y^2+4a^2=0.
\end{align}
\item Prove that the locus of the point of intersection of perpendicular normals
is the parabola 
\begin{align}
\vec{x}^T\myvec{0 & 0\\0 & 1}\vec{x}-a\myvec{1 & 0 }\vec{x}+ 3a^2 =0
\end{align}
\item Prove that if the tangents at two points on the parabola intersect in
the point $\myvec{x_1\\y_1}$, the corresponding normals intersect in the
point 
\begin{align}
\myvec{2a-x_1+\frac{y_1^2}{a}\\-\frac{x_1y_1}{a}}.
\end{align}
\item Show that, if the tangent at $\vec{P}$ meets the latus rectum in $\vec{K}$, then $SK$ is a mean
proportional between the segments of the focal chord through $\vec{P}$.
\item Show that, if the tangents from $\vec{Q}$ to the parabola form with the tangent at the vertex,
a triangle of constant area $c^2$, then the locus
of $\vec{Q}$ is the curve
\begin{align}
x^2\brak{y^2-4ax} = 4c^4.
\end{align}
\item Show that the normals at the ends of each of a series of parallel chords of a parabola intersect
on a fixed straight line, itself a normal to the parabola.
\item $\vec{P}$, $\vec{Q}$ are points on the parabola subtending a constant angle
$\alpha$ at the vertex.  Show that the locus of the intersection of the tangents
at $\vec{P}$, $\vec{Q}$ is the curve 
\begin{align}
\vec{x}^T\myvec{0 & 0\\0 & 1}\vec{x}-\myvec{4a + \frac{\tan^2\alpha}{4} & 0 }\vec{x}= a^2\tan^2\alpha 
\end{align}
\item Prove that the exterior angle between two tangents to a parabola is equal to the
angle which either of them subtends at the focus.
\item Two perpendicular focal chords of a parabola meet the directrix in $\vec{T}$ and $\vec{T}_1$.
Show that the tangents to the parabola which are parallel to these chords intersect in the middle point of $TT_1$.
\item Prove that, if the tangents at the points $\vec{Q}$, $\vec{R}$ intersect at $\vec{P}$, then 
\begin{align}
PQ^2:PR^2=SQ:SR
\end{align}
\item The tangents at any two points $\vec{P}$, $\vec{Q}$ meet at $\vec{T}$ and the normals meet at $\vec{N}$.  Prove that the projection
of $TN$ on the axis is equal to the sum of the distances of $\vec{P}$ and $\vec{Q}$ from the directrix.
\item Prove that the circumscribing circle of the triangle formed by three tangents to a parabola
passes through the focus.
\item $PQ$ is a chord of a parabola normal at $\vec{P}$; the circle on $PQ$ as diameter cuts the parabola again in $\vec{R}$.  Prove that the projection
of $QR$ on the axis is twice the latus rectum.
\item Prove that the distance between a tangent and the parallel normal is $a\text{cosec}\theta\sec^2\theta$, where $\theta$ is the
angle which either makes with the axis.
\item Prove that, if the normals at $\vec{P}$ and $\vec{Q}$ intersect on the curve, then $PQ$ cuts the axis in
a fixed point.
\item Prove that, if the normals at $\vec{P}$ and $\vec{Q}$ meet at the point $\vec{R}$ $\myvec{x_1,y_1}$ on the parabola, and the tangents at $\vec{P}$ and $\vec{Q}$
meet at $\vec{T}$, then
\begin{align}
TP.TQ=\frac{1}{2}\brak{x_1-8a}\sqrt{y_1^2+4a^2}.
\end{align}
\item Show that, in the last problem, as $\vec{R}$ moves along the parabola, the middle point of $PQ$
always lies on the parabola
\begin{align}
\label{eq:parab_standard}
\vec{x}^T\myvec{0 & 0\\0 & 1}\vec{x}-2a\myvec{1 & 0 }\vec{x}= 4a^2 
\end{align}
\item Prove that the area of the triangle formed by the tangents at the points $t_1,t_2$, and their chord of 
contact is
\begin{align}
\frac{1}{2}a^2\brak{t_1-t_2}^2
\end{align}
\item Prove that the area of the triangle formed by three points $t_1$, $t_2$, $t_3$ on the parabola is
\begin{align}
a^2\brak{t_2-t_3}\brak{t_3-t_1}\brak{t_1-t_2}
\end{align}
and that this is double the area of the triangle formed by the tangents at these points.
\item Prove that, if a line through any point $P \myvec{x_1\\y_1}$ making an angle $\theta$ with the axis meets the parabola
at $\vec{Q}$ and $\vec{R}$, then
\begin{align}
PQ.PR = \brak{y_1^2-4ax_1}\text{cosec}^2\theta.
\end{align}
\item Two chords $QR$, $Q_1R_1$ of a parabola meet at $\vec{O}$, and the diameters bisecting them meet the curve at $\vec{P}$ and $P_1$.  Prove that
\begin{align}
QO.OR:Q_1O.OR_1=SP:SP_1
\end{align}
\item Show that, if $\vec{P}$ is on the parabola, the length of the chord through $\vec{P}$ that makes an angle $\theta$ with the axis is
\begin{align}
4a\sin\brak{\alpha-\theta}\text{cosec}^2\theta\text{cosec}\alpha
\end{align}
where $\alpha$ is the inclination of the tangent at $\vec{P}$ to the axis.
\item Show that the locus of the middle point of a chord which passes through the fixed point $\myvec{h\\k}$ is the parabola
\begin{align}
\label{eq:parab_standard}
\vec{x}^T\myvec{0 & 0\\0 & 1}\vec{x}-\myvec{2a & k }\vec{x}+2ah= 0 
\end{align}
\item A tangent to the parabola 
\begin{align}
\vec{x}^T\myvec{0 & 0\\0 & 1}\vec{x}+4b\myvec{1 & 0 }\vec{x}= 0 
\end{align}
meets the parabola 
\begin{align}
\vec{x}^T\myvec{0 & 0\\0 & 1}\vec{x}-4a\myvec{1 & 0 }\vec{x}= 0 
\end{align}
at $\vec{P}$, $\vec{Q}$.  Prove that the locus of the middle point of $PQ$
is
\begin{align}
\vec{x}^T\myvec{0 & 0\\0 & 2a+b}\vec{x}-4a^2\myvec{1 & 0 }\vec{x}= 0 
\end{align}
\item Prove that the polar of the focus of a parabola is the directrix.
\item Prove that, if a chord of the parabola subtends a right angle at the vertex, the locus of its pole is 
\begin{align}
\myvec{1 & 0}\vec{x} + 4a= 0 
\end{align}
\item Show that, if parabolas 
\begin{align}
\vec{x}^T\myvec{0 & 0\\0 & 1}\vec{x}-4a\myvec{1 & 0 }\vec{x}= 0 
\end{align}
 are drawn corresponding to different values of $a$, the feet of the perpendiculars
from a fixed point on its polar lines all lie on a circle passing through the point.
\item Prove that, if from a point $\vec{Q}= \myvec{x_1\\y_1}$ a perpendicular be drawn to the polar
of $\vec{Q}$ with regard to the parabola cutting it in $\vec{R}$ and the axis in $G$, then
\begin{align}
SG=SR=x_1+a
\end{align}
\item Prove that, if the diameter through a point $\vec{P}$ of a parabola meets any chord in $\vec{O}$ and the tangents at the
ends of the chord in $\vec{T}, \vec{T}_1$, then
\begin{align}
PO^2=PT.PT_1
\end{align}
\item $QQ_1$ is a chord of a parabola and $TOR$ is a diameter which meets the tangent at $\vec{Q}$ in $\vec{T}$, the curve in $\vec{O}$ and $QQ_1$ in $\vec{R}$.  Prove
that 
\begin{align}
TO:OR=QR:RQ_1
\end{align}
\item Prove that if the normals at three points $\vec{P}$, $\vec{Q}$, $\vec{R}$ on a parabola concur, then the points $\vec{P}$, $\vec{Q}$, $\vec{R}$ and the vertex of
the parabola are concyclic.
\item Prove that in general, two members of the family of parabolas 
\begin{align}
\vec{x}^T\myvec{0 & 0\\0 & 1}\vec{x}-4a\myvec{1 & 0 }\vec{x}= 4a^2 
\end{align}
, where $a$ is the parameter specifying members
of the family, pass through any assigned point of the plane, and that these two parabolas cut orthogonally at $\vec{P}$.
\end{enumerate}
