\renewcommand{\theequation}{\theenumi}
\begin{enumerate}[label=\arabic*.,ref=\thesubsection.\theenumi]
\numberwithin{equation}{enumi}
%
\item Rain is falling vertically with a speed of 35 $m s^{-1}$
after sometime with a speed of 12 $m s^{-1}$
. Winds starts blowing in
east to west direction. In which direction should a boy waiting at a bus stop hold his umbrella ?
%
\item A motorboat is racing towards north at 25 km/h and the water current in that region is 10 km/h in the direction of 60$\degree$ east of south. Find the resultant velocity of the boat.
\item Rain is falling vertically with a speed of 35 $m s^{-1}$
. A woman rides a bicycle with a speed of 12 $ms^{-1}$ in east to west
direction. What is the direction in which she should hold her umbrella ?
\item  A hiker stands on the edge of a cliff 490 m above the ground and throws a stone horizontally with an initial speed of 15 $m s^{-1}$
. Neglecting air resistance,
find the time taken by the stone to reach the ground, and the speed with which it hits the ground. (Take g = 9.8 $m s^{-2}$
).
\item Rain is falling vertically with a speed of 30 $m s^{-1}$ of 10 $m s^{-1}$. A woman rides a bicycle with a speed in the north to south direction. What is the direction in which she should
hold her umbrella?
\item A man can swim with a speed of 4.0 km/h in still water. How long does he take to cross a river 1.0 km wide if the river flows steadily at 3.0 km/h and he makes his strokes normal to the river current? How far down the river does he go when he reaches the other bank ?
\item In a harbour, wind is blowing at the speed of 72 km/h and the flag on the mast of a boat anchored in the harbour flutters along the N-E direction. If the boat starts moving at a speed of 51 km/h to the north, what is the direction of the flag on the mast of the boat ?
\item A bullet fired at an angle of 30$\degree$ with the horizontal hits the ground 3.0 km away. By adjusting its angle of projection, can one hope to hit a target 5.0 km away ? Assume the muzzle speed to be fixed, and neglect air resistance.
\item  A fighter plane flying horizontally at an altitude of 1.5 km with speed 720 km/h passes directly overhead an anti-aircraft gun. At what angle from the vertical should the gun be fired for the shell with muzzle speed 600 $m s^{-1}$ to hit the plane ? 
At what minimum  altitude should the pilot fly the plane to avoid being hit ? (Take g = 10$ m s^{-2}$
).
\item Give the magnitude and direction of the net force acting on a stone of mass 0.1 kg, 
\item  just after it is dropped from the window of a stationary train, 
\item  just after it is dropped from the window of a train running at a constant velocity of 36 km/h,
\item  just after it is dropped from the window of a train accelerating with 1$ m s^{-2} $
\item  lying on the floor of a train which is accelerating with 1 m s-2, the stone being at rest relative to the train.
Neglect air resistance throughout. , 
\end{enumerate}
