\renewcommand{\theequation}{\theenumi}
\begin{enumerate}[label=\arabic*.,ref=\thesubsection.\theenumi]
\numberwithin{equation}{enumi}

	\item Solve 24x $<$ 100, when\\
	(i) x is a natural number.\\
	(ii) x is an integer.\\
	\item Solve -12x $>$ 30, when\\
	(i) x is a natural number.\\
	(ii) x is an integer.\\
	\item Solve 5x-3 $<$ 7, when\\
	(i) x is an integer.\\
	(ii) x is a real number.\\
	\item Solve 3x+8 $>$ 2, when\\
	(i) x is an integer.\\
	(ii) x is a real number\\
	
Solve the inequalities in Exercises 5 to 16 for real x.\\
	\item 4x+3 $<$ 5x+7.\\
	\item 3x-7 $>$ 5x-1.\\
	\item 3(x-1) $\geq$ 2(x-3).\\
	\item 3(2-x) $\leq$ 2(1-x).\\
	\item x+$\frac{x}{2}+\frac{x}{3}$ $<$ 11.\\
	\item $\frac{x}{3}\>\frac{x}{2}$+1.\\
	\item $\frac{3(x-2)}{5}\leq\frac{5(2-x)}{3}$.\\
	\item $ \frac{1}{2}$($\frac{3x}{5}$+4)$\geq\frac{1}{3}(x-6)$.\\
	\item 2(2x+3)-10 $<$ 6(x-2).\\
	\item 37-(3x+5) $\geq$ 9x-8(x-3).\\
	\item $\frac{x}{4}<\frac{(5x-2)}{3}-\frac{(7x-3)}{5}$.\\
	\item $\frac{(2x-1)}{3}\geq\frac{(3x-2)}{4}-\frac{(2-x)}{5}$.\\
	
Solve the inequalities in Exercises 17 to 20 and show the graph of the solution in each case on number line\\
    \item 3x-2 $<$ 2x+1.\\
    \item 5x-3 $\geq$ 3x-5.\\
    \item 3(1-x) $<$ 2(x+4).\\
    \item $\frac{x}{2}\geq\frac{(5x-2)}{3}-\frac{(7x-3)}{5}$.\\
    \item Ravi obtained 70 and 75 marks in first two unit test. Find the minimum marks he should get in the third test to have an average of at least 60 marks.\\
    \item To receive Grade A in a course, one must obtain an average of 90 marks or more in five examinations (each of 100 marks). If Sunita’s marks in first four examinations are 87, 92, 94 and 95, find minimum marks that Sunita must obtain in fifth examination to get grade ‘A’ in the course.\\
    \item Find all pairs of consecutive odd positive integers both of which are smaller than 10 such that their sum is more than 11.\\
    \item Find all pairs of consecutive even positive integers, both of which are larger than 5 such that their sum is less than 23.\\
    \item The longest side of a triangle is 3 times the shortest side and the third side is 2 cm shorter than the longest side. If the perimeter of the triangle is at least 61 cm, find the minimum length of the shortest side.\\
    \item A man wants to cut three lengths from a single piece of board of length 91cm.The second length is to be 3cm longer than the shortest and the third length is to be twice as long as the shortest. What are the possible lengths of the shortest board if the third piece is to be at least 5cm longer than the second?
[Hint: If x is the length of the shortest board, then x , (x + 3) and 2x are the
lengths of the second and third piece, respectively. Thus, x+(x+3)+2x $\leq$ 91 and 2x $\geq$ (x+3)+5].\\

Solve the following inequalities graphically in two-dimensional plane:
    \item x+y $<$ 5.\\
    \item 2x+y $\geq$ 6.\\    
    \item 3x+4y $\leq$ 12.\\
    \item y+8 $\geq$ 2x.\\
    \item x-y $\leq$ 2.\\
    \item 2x-3y $>$ 6.\\
    \item -3x+2y $\geq$ -6.\\
    \item 3y-5x $<$ 30.\\
    \item y $<$ -2.\\
    \item x $>$ -3.\\
   
Solve the following system of inequalities graphically:
    \item x $\geq$ 3, y $\geq$ 2.\\
    \item 3x+2y $\leq$ 12, x $\geq$ 1, y $\geq$ 2.\\
    \item 2x+y $\geq$ 6, 3x+4y $\leq$ 12.\\
    \item x+y $\geq$ 4, 2x-y $<$ 0.\\
    \item 2x-y $>$ 1, x-2y $<$ -1.\\
    \item x+y $\leq$ 6, x+y $\geq$ 4.\\
    \item 2x+y $\geq$ 8, x+2y $\geq$ 10.\\
    \item x+y $\leq$ 9, y $>$ x, x $\geq$ 0.\\
    \item 5x+4y $\leq$ 20, x $\geq$ 1, y $\geq$ 2.\\
    \item 3x+4y $\leq$ 60, x+3y $\leq$ 30, x $\geq$ 0, y $\geq$ 0.\\
    \item 2x+y $\geq$ 4, x+y $\leq$ 3, 2x-3y $\leq$ 6.\\
    \item x-2y $\leq$ 3, 3x+4y $\geq$ 12, x $\geq$ 0, y $\geq$ 1.\\
    \item 4x+3y $\leq$ 60, y $\geq$ 2x, x $\geq$ 3, x,y $\geq$ 0.\\
    \item 3x+2y $\leq$ 150, x+4y $\leq$ 80, x $\leq$ 15, y $\geq$ 0,\\
    x $\geq$ 0. \\    
    \item x+2y $\leq$ 10, x+y $\geq$ 1,x-y $\leq$ 0, x $\geq$ 0, \\
    y $\geq$ 0.\\
    
 Solve the inequalities in Exercises 52 to 57.\\
 
    \item 2 $\leq$ 3x-4 $\leq$ 5.\\
    \item 6 $\leq$ -3(2x-40)  $<$ 12.\\
    \item -3 $\leq$ 4-$\frac{7x}{2} \leq 18$.\\ 
    \item -15 $<$ $\frac{3(x-2)}{5} \leq 0$.\\
    \item -12 $<$ 4-$\frac{3x}{-5} \leq$ 2.\\
    \item 7 $\leq$ $\frac{(3x+11)}{2} \leq 11$.\\
    
Solve the inequalities in Exercises 58 to 61 and represent the solution graphically on number line. 
    \item 5x+1 $>$ -24, 5x-1 $<$ 24.\\
    \item 2(x-1) $<$ x+5, 3(x+2) $>$ 2-x.\\
    \item 3x-7 $>$ 2(x-6), 6-x $>$ 11-2x.\\
    \item 5(2x-7)-3(2x+3) $\leq$ 0, 2x+19 $\leq$ 6x+47.\\
    \item A solution is to be kept between 68$\degree$F and 77$\degree$F. What is the range in temperature in degree Celsius(C) if the Celsius / Fahrenheit(F) conversion formula is given by\\
    F= $\frac{9}{5}$ C+32?\\
    \item A solution of 8$\%$ boric acid is to be diluted by adding a 2$\%$ boric acid solution to
it. The resulting mixture is to be more than 4$\%$ but less than 6$\%$ boric acid. If we have
640 litres of the 8$\%$ solution, how many litres of the 2$\%$ solution will have to be added?\\
    \item How many litres of water will have to be added to 1125 litres of the 45$\%$ solution
of acid so that the resulting mixture will contain more than 25$\%$ but less than 30$\%$ acid
content?\\
    \item IQ of a person is given by the formula\\
            IQ = $\frac{MA}{CA}\times 100$,\\
    where MA is mental age and CA is chronological age.If 80 $\leq$ IQ $\leq$ 140 for a group of
12 years old children, find the range of their mental age.
    
    \end{enumerate}
