\item Let D be an interior point of the side BC of a triangle ABC. Let $I_1$ and $I_2$ be the incentres of triangles ABD and ACD respectively. Let $AI_1$ and $AI_2$ meet BC in E and F respectively. If $\angle BI_1E = 60^{o}$, what is the measure of $\angle CI_2F$ in degrees?

\item Let ABC ba an acute-angled triangle and let H be its orthocentre. Let $G_1$, $G_2$ and $G_3$ be the centroids of the triangles HBC, HCA and HAB respectively. If the area of the triangle $G_1G_2G_3$ is 7 units, what is the area of the triangle ABC?

\item Triangles ABC and DEF are such that $\angle A = \angle D$, AB  = DE = 17, BC = EF = 10  and AC - DF = 12. What is AC + DF?

\item In a triangle ABC, right-angled at A, the altitude through A and the internal bisector of $\angle A$ have lengths 3 and 4 respectively. Find the length of the median through A?

\item In a triangle ABC, the median from B to CA is perpendicular to the median from C to AB. If the median from A to BC is 30, determine $(BC^2 + CA^2 + AB^2)/100$.

\item Let AB be a chord of a circle with centre O. Let C be a point on the circle such that $\angle ABC = 30^{o}$ and O lies inside the triangle ABC. Let D be a point on AB such that $\angle DCO = \angle OCB = 20^{o}$. Find the measure of 
$\angle CDO$ in degrees.

\item Let ABCD be a trapezium in which AB$||$ CD and AD $\perp$ AB. Suppose ABCD has  an incircle which touches AB at Q and CD at P. Given that PC = 36 and QB = 49, find PQ.

\item In a quadrilateral ABCD, it is given that AB = AD = 13, BC = CD = 20, BD = 24. If r is the radius of the circle inscribable, then what is the integer closest to r?