\item Let ABC be a triangle and let $\Omega$ be its circumcircle. The internal bisectors of angles A, B and C intersect
$\Omega$ at $A_1$,$B_1$, and $C_1$, respectively, and the internal bisectors of angle $A_1$,$B_1$, $C_1$ of the the triangle $A_1B_1C_1$ intersect $\Omega$ at $A_2$,$B_2$, and $C_2$, respectively. If the smallest angle of triangle ABC is 
$40^{o}$, What is the magnitude of the smallest angle of triangle $A_2B_2C_2$.

\item How many distinct triangles ABC are there, upto similarity, such that the magnitudes of angles A, B, and C in degrees are positive ibtegers and satisfy
\begin{align*}
\cos A \cos B + \sin A \sin B \sin kC = 1
\end{align*}
for some positive integer k, where kC does not exceed $360^{o}$?

\item In how many ways can a pair of parallel diagonals of a regular polygon of 10 sides be selected?

\item Let AB be a diameter of a circle and let C be a point on the segment AB such that AC : CB = 6 : 7. Let D be a point on the circle such that DC is perpendicular to AB. Let DE be the diameter through D. If [XYZ] denote the area of the triangle XYZ, find $[ABD]/[CDE]$to the nearest integer?

\item Let ABCD be a convex cuclic quadrilateral. Suppose P is a point in the plane of the quadrilateral such that the sum of its distances from the vertices ABCD is the least. If
\begin{align*}
\{PA, PB, PC, PD\} = \{3, 4, 6, 8\}
\end{align*}
What is the maximum possible area of ABCD?

\item Let ABC be a triangle with sides 51, 52, 53. Let $\Omega$ denote the incircle of $\Delta ABC$. Draw tangents to $\Omega$ which are parallel to the sides of ABC. Let $r_1$, $r_2$, $r_3$ be the inradii of the three corner triangles so formed. Find the largest integer that does not exceed $r_1 + r_2 + r_3$?

\item In a triangle ABC, the median, the median AD(with D and BC) and the angle bisector BE(with E on AC) are perpendicular to each other. If AD = 7, and BE = 9, find the integer nearest to the area of triangle ABC.