\renewcommand{\theequation}{\theenumi}
\begin{enumerate}[label=\arabic*.,ref=\thesubsection.\theenumi]
\numberwithin{equation}{enumi}

\item A bus starting from rest moves with a uniform acceleration of $0.1 m s^{-2}$
for 2 minutes. Find 

\begin{enumerate} 
\item the speed acquired, 
\item the distance travelled.
\end{enumerate}

\item A train is travelling at a speed of $90 km h^{-1}$
. Brakes are applied . Find
so as to produce a uniform acceleration of $- 0.5 m s^{-2}$
how far the train will go before it is brought to rest.
\item  A trolley, while going down an inclined plane, has an acceleration of $2 cm s^{-2}$
. What will
be its velocity $3 s$ after the start? . What
\item  A racing car has a uniform acceleration of $4 m s^{-2}$
distance will it cover in $10 s$ after start?
\item  A stone is thrown in a vertically upward direction with a velocity of $5 m s^{-1}$
. If the acceleration of the
stone during its motion is $10 m s^{-2}$ in the downward direction, what will be the height attained by the stone and how much time will it take to reach there?

\item An athlete completes one round of a circular track of diameter 200 m in 40 s. What will be the distance covered and the displacement at the end of 2 minutes 20 s?
\item  Joseph jogs from one end A to the other end B of a straight 300 m road in 2 minutes 30 seconds and then turns around
and jogs 100 m back to point C in another 1 minute. What are Joseph’s average speeds and velocities in jogging 

\begin{enumerate} 
\item from A to B and 
\item from A to C?
\end{enumerate}

\item  Abdul, while driving to school, computes the average speed for his trip to be 20 $km h^{-1}$
. On his return trip along the same
route, there is less traffic and the average speed is 30 $km h^{-1}$
. What is the average speed for Abdul’s trip?
\item  A motorboat starting from rest on a lake accelerates in a straight line at a constant rate of 3.0 $m s^{-2}$
for 8.0 s. How far does the boat travel during this time? 
\item  A driver of a car travelling at 52 $km h^{-1}$
applies the brakes and in another car applies
accelerates uniformly in the opposite direction. The car stops in 5 s. Another driver going at 3 $km h^{-1}$
his brakes slowly and stops in 10 s. On the same graph paper, plot the speed versus time graphs for the two cars. Which of the two cars travelled farther after the brakes were applied?

\item A ball is gently dropped from a height of 20 m. If its velocity increases uniformly at the rate of 10 $m s^{-2}$
, with what velocity
will it strike the ground? After what time will it strike the ground?

\item An artificial satellite is moving in a circular orbit of radius 42250 $km$. Calculate its speed if it takes 24 hours to revolve around the earth.
\item From a rifle of mass 4 kg, a bullet of mass 50 g is fired with an initial velocity of 35 $m s^{-1}$
.
Calculate the initial recoil velocity of the rifle.
\item Two objects of masses 100 g and 200 g are moving along the same line and direction with velocities of 2 $m s^{-1}$ and 1 $m s^{-1}$ , respectively. 
They collide and after the collision, the first object moves at a velocity of 1.67 $m s^{-1}$ 
. Determine the velocity of the second object.

\item A truck starts from rest and rolls down a hill with a constant acceleration. It travels a distance of 400 m in 20 s. Find its acceleration. Find the force acting on it if its mass is 7 tonnes (Hint: 1 tonne = 1000 kg.)
\item  A stone of 1 kg is thrown with a velocity of 20 $m s^{-1}$ across
the frozen surface of a lake and comes to rest after travelling a distance of 50 m. What is the force of friction between the stone and the ice?
\item  A 8000 kg engine pulls a train of 5 wagons, each of 2000 kg, along a horizontal track. If the engine exerts a force of 40000 N and the track offers a friction force of 5000 N, then calculate: 
\begin{enumerate} 
\item the net accelerating force and 
\item the acceleration of the train.
\end{enumerate}
\item  An automobile vehicle has a mass of 1500 kg. What must be the force between the vehicle and road if the vehicle is to
be stopped with a negative acceleration of 1.7 $m s^{-2}$ 
\item  Using a horizontal force of 200 N, we intend to move a wooden cabinet across a floor at a constant velocity. What is the friction force that will be exerted on the cabinet?
\item  Two objects, each of mass 1.5 kg, are moving in the same straight line but in opposite directions. The velocity of each object is 2.5 $m s^{-1}$
before the collision during which they stick together. What will be the velocity of the combined object after collision?
\item A hockey ball of mass 200 g travelling at 10 $m s^{-1}$ is struck by
a hockey stick so as to return it along its original path with a velocity at 5 $m s^{-1}$
momentum occurred in the motion of the hockey ball by the force applied by the hockey stick.
\item  A bullet of mass 10 g travelling horizontally with a velocity of 150 $m s^{-1}$
strikes a stationary wooden block and comes to rest in 0.03 s. Calculate the distance of penetration of the bullet into the block. Also calculate the magnitude of the force exerted by the wooden block on the bullet.
\item  An object of mass 1 kg travelling in a straight line with a velocity of 10 $m s^{-1}$
collides with, and sticks to, a stationary wooden block of mass 5 kg. Then they both move off together in the same straight line. Calculate the total momentum just before the impact and just after the impact. Also, calculate the velocity of the combined object.
\item  An object of mass 100 kg is accelerated uniformly from a velocity of 5 $m s^{-1}$
to 8 $m s^{-1}$ in 6 s. Calculate the initial and final
momentum of the object. Also, find the magnitude of the force exerted on the object.
\item  How much momentum will a dumb-bell of mass 10 kg transfer to the floor if it falls from a height of 80 cm? Take its downward acceleration to be 10 $m s^{-2}$. Calculate the magnitude of change of

\item Two persons manage to push a motorcar of mass 1200 kg at a uniform velocity along a level road. The same motorcar can be pushed by three persons to produce an acceleration of 0.2 $m s^{-2}$
. With what force does each person push the motorcar? (Assume that all persons push the motorcar with the same muscular effort.)
\item  A hammer of mass 500 g, moving at 50 $m s^{-1}$ , strikes a nail.
The nail stops the hammer in a very short time of 0.01 s. What is the force of the nail on the hammer?
\item  A motorcar of mass 1200 kg is moving along a straight line with a uniform velocity of 90 km/h. Its velocity is slowed down to 18 km/h in 4 s by an unbalanced external force. Calculate the acceleration and change in momentum. Also calculate the magnitude of the force required.
\item What is the magnitude of the gravitational force between the earth and a 1 kg object on its surface? (Mass of the earth is 6 $\times$ 1024 kg and radius of the earth is 6.4 $\times$ 106 m.)
\item A ball is thrown vertically upwards with a velocity of 49 m/s. Calculate

\begin{enumerate} 
\item  the maximum height to which it rises, 
\item the total time it takes to return to the surface of the earth.
\end{enumerate}

\item  A stone is released from the top of a tower of height 19.6 m. Calculate its final velocity just before touching the ground.
\item  A stone is thrown vertically upward with an initial velocity of 40 m/s. Taking g = 10 $ms^{-2}$
, find the maximum height reached
by the stone. What is the net displacement and the total distance covered by the stone?
\item  Calculate the force of gravitation between the earth and the Sun, given that the mass of the earth = 6 $\times 10^{24}$
kg and of the
Sun = 2 $\times 10^{30}$ kg. The average distance between the two is 1.5 $\times 10^{11}$
m.
\item  A stone is allowed to fall from the top of a tower 100 m high and at the same time another stone is projected vertically upwards from the ground with a velocity of 25 m/s. Calculate when and where the two stones will meet.
\item  A ball thrown up vertically returns to the thrower after 6 s. Find
\begin{enumerate} 
\item the velocity with which it was thrown up, 
\item the maximum height it reaches, and 
\item  its position after 4 s.
\end{enumerate}

\item The volume of 50 g of a substance is 20 $cm^3$ 
. If the density of water is 1 $g cm^{-3}$, will the substance float or sink? 
\item  The volume of a 500 g sealed packet is 350 $cm^3$
Will the packet float or sink in water if the density of water is 1 $g cm^{-3}$ ? What will be the mass of the water displaced by this packet?
\item Certain force acting on a 20 kg mass changes its velocity from 5 $m s^{-1}$
to 2 $m s^{-1}$. Calculate the work done by the force.
\item A certain household has consumed 250 units of energy during a month. How much energy is this in joules?
\item  An object of mass 40 kg is raised to a height of 5 m above the ground. What is its potential energy? If the object is allowed to fall, find its kinetic energy when it is half-way down.
\item An electric heater is rated 1500 W. How much energy does it use in 10 hours?
\item Calculate the work required to be done to stop a car of 1500 kg moving at a velocity of 60 km/h?
\item Find the energy in kW h consumed in 10 hours by four devices of power 500 W each.
\item An echo is heard in 3 s. What is the distance of the reflecting surface from the source, given that the speed of sound is 342 $m s^{-1}$
?  
\item A submarine emits a sonar pulse, which returns from an underwater cliff in 1.02 s. If the speed of sound in salt water is 1531 m/s, how far away is the cliff?
\item A person has a hearing range from 20 Hz to 20 kHz. What are the typical wavelengths of sound waves in air corresponding to these two frequencies? Take the speed of sound in air as 344 $m s^{-1}$
.
\item Two children are at opposite ends of an aluminium rod. One strikes the end of the rod with a stone. Find the ratio of times taken by the sound wave in air and in aluminium to reach the second child.
\item  The frequency of a source of sound is 100 Hz. How many times does it vibrate in a minute?
\item A stone is dropped from the top of a tower 500 m high into a pond of water at the base of the tower. When is the splash heard at the top? Given, g = 10 $m s^{-2}$
and speed of sound = 340 $m s^{-1}$ . 
\item  A sound wave travels at a speed of 339 $m s^{-1}$ 174 . If its
wavelength is 1.5 cm, what is the frequency of the wave? Will it be audible?
\item A sonar device on a submarine sends out a signal and receives an echo 5 s later. Calculate the speed of sound in water if the distance of the object from the submarine is 3625 m.
\item An object 5 cm in length is held 25 cm away from a converging lens of focal length 10 cm. Draw the ray diagram and find the position, size and the nature of the image formed.
\item  A concave lens of focal length 15 cm forms an image 10 cm from the lens. How far is the object placed from the lens? Draw the ray diagram.
\item  An object is placed at a distance of 10 cm from a convex mirror of focal length 15 cm. Find the position and nature of the image.
\item  The magnification produced by a plane mirror is +1. What does this mean? 
\item  An object 5.0 cm in length is placed at a distance of 20 cm in front of a convex mirror of radius of curvature 30 cm. Find the position of the image, its nature and size.
\item  An object of size 7.0 cm is placed at 27 cm in front of a concave mirror of focal length 18 cm. At what distance from the mirror should a screen be placed, so that a sharp focussed image can be obtained? Find the size and the nature of the image.
\item  Find the focal length of a lens of power - 2.0 D. What type of lens is this? 
\item  A doctor has prescribed a corrective lens of power +1.5 D. Find the focal length of the lens. Is the prescribed lens diverging or converging?
\item  Judge the equivalent resistance when the following are connected in parallel - 
\begin{enumerate} \item 1 $\ohm $ and $10^6 \ohm $, \item1 $\ohm $ and $10^3 \ohm$, and $10^6 \ohm$.\end{enumerate}
\item An electric lamp of 100 $\ohm$, a toaster of resistance 50 $\ohm$, and a water filter of resistance 500 $\ohm $ are connected in parallel to a 220 V source. What is the resistance of an electric iron connected to the same source that takes as much current as all three appliances, and what is the current through it?
\item  How can three resistors of resistances 2 $\ohm$, 3 $\ohm$, and 6 $\ohm$ be connected to give a total resistance of
 \begin{enumerate} \item 4 $\ohm$, \item 1 $\ohm$ \end{enumerate}?
\item What is 
\begin{enumerate} \item the highest, \item the lowest total resistance 
\end{enumerate}
that can be secured by combinations of four coils of resistance 4 $\ohm$, 8 $\ohm$, 12 $\ohm$, 24 $\ohm$?
\item  A piece of wire of resistance R is cut into five equal parts. These parts are then connected in parallel. If the equivalent resistance of this combination is R', then the ratio R/R' is -
%\begin{enumerate} \item 1/25 R \item 1/5 \item IR2 \item  5 \item  VI \item  25
%\end{enumerate}
\item  An electric bulb is rated 220 V and 100 W. When it is operated on 110 V, the power consumed will be - 
\item  Two conducting wires of the same material and of equal lengths and equal diameters are first connected in series and then parallel in a circuit across the same potential difference. The ratio of heat produced in series and parallel combinations would be -
\item  A copper wire has diameter 0.5 mm and resistivity of 1.6 $\times 10^{-8} \ohm$ m. What will be
the length of this wire to make its resistance 10 $\ohm$? How much does the resistance change if the diameter is doubled?
%\item  The values of current I flowing in a given resistor for the corresponding values of potential difference V across the resistor are given below - I (amperes) 0.5 1.0 2.0 V (volts)
%\item 0 1.6 3.4 6.7 10.2 4.0 13.2 Plot a graph between V and I and calculate the resistance of that resistor.
\item  When a 12 V battery is connected across an unknown resistor, there is a current of 2.5 mA in the circuit. Find the value of the resistance of the resistor.
\item  A battery of 9 V is connected in series with resistors of 0.2 $\ohm$, 0.3 $\ohm$, 0.4 $\ohm$ , 0.5 $\ohm$ and 12 $\ohm$, respectively. How much current would flow through the 12 $\ohm$ resistor?
\item  How many 176 $\ohm$ resistors (in parallel) are required to carry 5 A on a 220 V line? 
\item  Show how you would connect three resistors, each of resistance 6 $\ohm$, so that the combination has a resistance of \begin{enumerate} \item  9 $\ohm$, \item 4 $\ohm$.\end{enumerate}
\item  Several electric bulbs designed to be used on a 220 V electric supply line, are rated 10 W. How many lamps can be connected in parallel with each other across the two wires of 220 V line if the maximum allowable current is 5 A?
\item  A hot plate of an electric oven connected to a 220 V line has two resistance coils A and B, each of 24 $\ohm$ resistance, which may be used separately, in series, or in parallel. What are the currents in the three cases?
\item  Compare the power used in the 2 $\ohm$ resistor in each of the following circuits: \begin{enumerate} \item  a 6 V battery in series with 1 $\ohm$ and 2 $\ohm$ resistors, and \item a 4 V battery in parallel with 12 $\ohm$ and 2 $\ohm$ resistors.\end{enumerate}
\item Two lamps, one rated 100 W at 220 V, and the other 60 W at 220 V, are connected in parallel to electric mains supply. What current is drawn from the line if the supply voltage is 220 V?
\item Which uses more energy, a 250 W TV set in 1 hr, or a 1200 W toaster in 10 minutes? 
\item  An electric heater of resistance 8 $\ohm$ draws 15 A from the service mains 2 hours. Calculate the rate at which heat is developed in the heater.
\end{enumerate}
%\end{enumerate}
%\end{document}
