\renewcommand{\theequation}{\theenumi}
\begin{enumerate}[label=\arabic*.,ref=\thesection.\theenumi]
\numberwithin{equation}{enumi}
%
%
\item An object travels 16m in 4s and then another 16 m in 2 s. What is the average speed of the object?
\item The odometer of a car reads 2000 km at the start of a tri and 2400 km at the end of the trip.  If the trip took 8 h, calculat the average speed of the car in km/h and m/s.
\item Usha swims in a 90m long pool.  She covers 180m in one minute by swimming from one end to the other and back along the same straight path.  Find the average speed and average velocity of Usha.
\item Starting from a stationary position, Rahul paddles his bicycle to
attain a velocity of $6 m s^{-1}$ in $30 s$. Then
he applies brakes such that the velocity of the bicycle comes down to $4 m s^{-1}$
the next $5 s$. Calculate the acceleration of the bicycle in both the cases
%
\item A train starting from rest attains a velocity of $72 km h^{-1}$
in
5 minutes. Assuming that the acceleration is uniform, find (i) the acceleration and (ii) the distance travelled by the train for attaining this velocity.
%
\item A car accelerates uniformly from $18 km h
^{-1}$ to $36 km h^{-1}$ in $5 s$. 
Calculate 
\begin{enumerate}
\item the acceleration and 
\item  the distance covered by the car in that time.
\end{enumerate}
%
\item The brakes applied to a car produce an acceleration of $6 m s^{-2}$
in
the opposite direction to the motion. If the car takes $2 s$ to stop after the application of brakes, calculate the distance it travels during this time.
%
\item A constant force acts on an object of mass 5 kg for a duration of 2 s. It increases the object’s velocity from 3 $m s^{-1}$
to 7 $m s^{-1}$ . Find the
magnitude of the applied force. Now, if the force was applied for a duration of 5 s, what would be the final velocity of the object?
\item Which would require a greater force -- accelerating a 2 kg mass at 5 $m s^{-2}$
or a 4 kg mass at 2 $m s^{-2}$?
\item A motorcar is moving with a velocity of 108 km/h and it takes 4 s to stop after the brakes are applied. Calculate the force exerted by the brakes on the motorcar if its mass along with the passengers is 1000 kg.
\item A force of 5 N gives a mass m1
, an acceleration of 10 $m s^{-2}$ mass m2, an acceleration of 20 $m s^{-2}$
and a .
What acceleration would it give if both the masses were tied together?
\item A bullet of mass 20 g is horizontally fired with a velocity 150 $m s^{-1}$
What is the recoil velocity of the pistol?
\item A girl of mass 40 kg jumps with a horizontal velocity of 5 $m s^{-1}$
onto
a stationary cart with frictionless wheels. The mass of the cart is 3 kg. What is her velocity as the cart starts moving? Assume that there is no external unbalanced force working in the horizontal direction.
\item Two hockey players of opposite teams, while trying to hit a hockey ball on the ground collide and immediately become entangled. One has a mass of 60 kg and was moving with a velocity 5.0 $m s^{-1}$
while the other
has a mass of 55 kg and was moving faster with a velocity 6.0 $m s^{-1}$
towards
the first player. In which direction and with what velocity will they move after they become entangled? Assume that the frictional force acting between the feet of the two players and ground is negligible.

\item The mass of the earth is 6 $\times$ 1024
kg. If the distance between the earth and the moon is 3.84$\times$105
7.4 $\times$ 1022
calculate the force exerted by the earth on the moon. (Take G = 6.7 $\times 10^{-11}
N m^2$ 
\item A car falls off a ledge and drops to the ground in 0.5 s. 
\begin{enumerate}
\item  What is its speed on striking the ground?
\item  What is its average speed during the 0.5 s?
\item  How high is the ledge from the ground?
\end{enumerate}
Let $g = 10 m s^{-2}$.
\item An object is thrown vertically upwards and rises to a height of 10 m. Calculate (i) the velocity with which the object was thrown upwards and (ii) the time taken by the object to reach the highest point. Let $g = 9.8 m s^{-2}$.
\item Mass of an object is 10 kg. What is its weight on the earth?
\item An object weighs 10 N when measured on the surface of the earth. What would be its weight when measured on the surface of the moon?
\item A block of wood is kept on a tabletop. The mass of wooden block is 5 kg and its dimensions are 40 cm $\times$ 20 cm $\times$ 10 cm. Find the pressure exerted by the wooden block on the table top if it is made to lie on the table top with its sides of dimensions (a) 20 cm $\times$ 10 cm and (b) 40 cm $\times$ 20 cm.
\item Relative density of silver is 10.8. The density of water is $103
kg m^{-3}$.  What is the density of silver in SI unit? 
\item A force of 7 N acts on an object. The displacement is, say 8 m, in the direction of the force. Let us take it that the force acts on the object through the displacement. What is the work done in this case?
\item A porter lifts a luggage of 15 kg from the ground and puts it on his head 1.5 m above the ground. Calculate the work done by him on the luggage.
\item An object of mass 15 kg is moving with a uniform velocity of 4
$m s^{-1}$ 
. What is the kinetic energy possessed by the object?
\item What is the work to be done to increase the velocity of a car from 30 $km h^{-1}$
to 60 $km h^{-1}$ the car is 1500 kg? 
\item The kinetic energy of an object of mass, m moving with a velocity of 5 $m s^{-1}$
is 25 J. What will be its
kinetic energy when its velocity is doubled? What will be its kinetic energy when its velocity is increased three times?
\item  Find the energy possessed by an object of mass 10 kg when it is at a height of 6 m above the ground. Given, g = 9.8 $m s^{-2}$
.
\item An object of mass 12 kg is at a certain height above the ground. If the potential energy of the object is 480 J, find the height at which the object is with respect to the ground. Given, g = 10 $m s^{-2}$.
\item Two girls, each of weight 400 N climb up a rope through a height of 8 m. We name one of the girls A and the other B. Girl A takes 20 s while B takes 50 s to accomplish this task. What is the power expended by each girl?
\item A boy of mass 50 kg runs up a staircase of 45 steps in 9 s. If the height of each step is 15 cm, find his power. Take g = 10 $m s^{-2}$
.
\item An electric bulb of 60 W is used for 6 h per day. Calculate the 'units' of energy consumed in one day by the bulb.
\item A sound wave has a frequency of 2 kHz and wave length 35 cm. How long will it take to travel 1.5 km?
\item A person clapped his hands near a cliff and heard the echo after 2 s. What is the distance of the cliff from the person if the speed of the sound, v is taken as 346 $m s^{-1}$?
\item A ship sends out ultrasound that returns from the seabed and is
detected after 3.42 s. If the speed of ultrasound through seawater is 1531 m/s, what is the distance of the seabed from the ship?
\end{enumerate}
