\item Let AD and BC be the parallel sides of a trapezium ABCD. Let P and Q be the midpoints of the diagonals AC and BD. If $AD = 16$ and $BC = 20$, What is the length of PQ?

\item In a triangle ABC, let H, I and O be the orthocentre, incentre and circumcentre, respectively. If the points B, H, I, C lie on a circle, What is magnitude of $\angle BOC$ in degrees?

\item Let ABC be an equilateral triangle. Let P and S be points on AB and AC,respectively, and let Q and R be points on BC such that PQRS is a triangle. If $PQ = \sqrt{3}PS$ and the area of PQRS is $28\sqrt{3}$, What is the length of PC?

\item Let $A_1, B_1, C_1, D_1$ be the midpoints of the sides of a convex quadrilateral ABCD and let $A_1, B_2, C_2, D_2$ be the midpoints of the quadrilateral $A_1B_1C_1D_1$. If $A_2B_2C_2D_2$ is a rectangle with sides 4 and 6, then what is the product of the lengths of the diagonals of ABCD?

\item Let S be a circle with centre O. A chord AB, not a diameter, divides S into two regions $R_1$ and $R_2$ such that O belongs to $R_2$. Let $S_1$ be a circle with centre in $R_1$, touching AB at X and S internally. Let $S_2$ be a circle with centre in $R_2$, touching AB at Y, the circle S internally and passing through the centre of S. The point X lies on the diameter passing through the centre of  $S_2$ and $\angle YXO = 30^O$. If the radius of $S_2$ is 100 then what is the radius of $S_1$?

\item In a triangle ABC with $\angle BCA = 90^{o}$, the perpendicular bisector of AB intersects segments AB and AC at X and Y, respectively. If the ratio of the area of quadrilateral BXYC to the area of triangle ABC is 13 : 18 and BC = 12 then what is the length of AC?
