\item From a square with sides of length 5, triangular pieces from the four corners are removed to form a regular octagon. Find the area removed to the nearest integer?

\item Let ABC be a triangle and let $\Omega$ be its circumcircle. The internal bisectors of angles A, B and C intersect 
$\Omega$ at $A_1, B_1$, and $C_1$, respectively, and the internal bisectors of angles $A_1, B_1$, and $C_1$, of the triangle $A_1B _1 C_1$, intersect $\Omega$ at $A_2, B_2$, and $C_2$, respectively. If the smallest angle of triangle ABC is $40^{o}$, what is the magnitude of the smallest angle of triangle $A_2 B_2 C_2$, in degrees?

\item Let AB be a diameter of a circle and let C be a point on the segment AB such that AC : CB = 6 : 7. Let D be a point on the circle such that DC is perpendicular to AB. Let DE be the diameter through D. If [XYZ] denotes the area of the triangle XYZ, find [ABD]/[CDE] to the nearest integer.

\item Let ABCD be a convex cyclic quadrilateral. Suppose P is a point in the plane of the quadrilateral such that the sum of its distances from the vertices of ABCD is the least. If (PA, PB, PC, PD) = (3, 4, 6, 8), What is the maximum possible area of ABCD?

\item Let ABC be a triangle with sides 51, 52, 53. Let $\Omega$ denote the incircle of $\triangle ABC$. Draw tangents to
$\Omega$ which are parallel to the sides of ABC. Let $r_{1}, r_{2}, r_{3}$ be the inradii of the three corner triangles so formed. Find the largest integer that does not exceed $r_1 + r_2 + r_3$.

\item In a triangle ABC, the median AD (with D on BC) and the angle bisector BE (with E on AC) are perpendicular to each other. If AD = 7 and BE = 9, find the integer nearest to the area of triangle ABC.
