\item Let $f(x) = x^2 + ax + b$. If for all nonzero real x
\begin{align*}
f(x + \frac{1}{x}) = f(x) + f(\frac{1}{x})
\end{align*}
and the roots of f(x) = 0 are integers, what is the value of $a^2 + b^2$?

\item Let $x_{1}$ be a positive real number and for every integer $n \geq 1$ let 
\begin{align*}
x_{n+1}  1 + x_1 x_2..........x_{n-1}x_n
\end{align*}
If $x_{5} = 43$, what is the sum of digits of the largest prime factor of $x_{6}$?

\item Let $\overline{abc}$ be a three digit number with nonzero digits such that $a^2 + b^2 = c^2$. What is the largest possible prime factor of $\overline{abc}$?

\item On a clock, there are two instants between 12 noon and 1 PM, when the hour hand and the minute hand are at right angles. The difference in minutes between these two instants is written as $a + \frac{b}{c}$, where a, b, c are positive integers, with $b < c$ and $\frac{b}{c}$ in the reduced form. Whatis the value of a + b + c?

\item How many positive integers n are there such that $3 \leq n \leq 100$ and $ x^{2^{n}} + x + 1$ is divisible by 
$x^{2} + x + 1$?

\item Let the rational number $\frac{p}{q}$ be closest to but not equal to $\frac{22}{7}$ among all rational numbers with denominator $ < 100$. What is the value of p - 3q?

\item A natural number $k > 1$ is called good if there exist natural numbers
\begin{align*}
a_{1} < a_{2} <...... < a_{k}
\end{align*}
such that 
\begin{align*}
\frac{1}{\sqrt{a_1}} + \frac{1}{\sqrt{a_2}} +.......+ \frac{1}{\sqrt{a_k}} = 1
\end{align*}
Let f(n) be the sum of the first n good numbers, $n \geq 1$. Find the sum of all values of n for which f(n + 5)/f(n) is an integer.

\item Each of the numbers $x_1, x_2,........, x_{101}$ is $\pm$ 1. What is the smallest positive value of 
\begin{align*}
\sum_{1 \leq i < j \leq 101} x_{i} x_{j}.
\end{align*}

\item Find the smallest positive integer $n \geq 10$ such that n + 6 is a prime and 9n + 7 is a perfect square.

\item Find the number of ordered triples (a, b, c) of positive integers such that $30a + 50b + 70c \leq 343$

\item How many ordered pairs (a, b) of positive integers with $a < b$ and $100 \leq a, b \leq 1000$ satisfy gcd(a, b) : lcm(a, b) = 1 : 495?

\item What is the greatest integer not exceeding the sum
\begin{align*} 
\sum_{n=1}^{1599} \frac{1}{\sqrt{n}}.
\end{align*}

\item Let E denote the set of all natural numbers n such that $3 < n < 100$ and the set \{1, 2, 3,......, n\} can be partitioned in to 3 subsets with equal sums. Find the number of elements of E.

\item Positive integers x, y, z satisfy xy + z = 160. Compute the smallest possible value of x + yz.