\item Let R be the set of real numbers. Determine all functions f : R $ \rightarrow $ R such that, for
all real numbers x and y,
\begin{align*}
f(f(x)f(y)) + f(x + y) = f(xy).
\end{align*}

\item A hunter and an invisible rabbit play a game in the Euclidean plane. The rabbit’s starting point, $A_0$, and the hunter’s starting point, $B_0$, are the same. After n-1 rounds of the game,the rabbit is at point $A_{n-1}$ and the hunter is at point $B_{n-1}$. In the $n^{th}$ round of the game, three things occur in order.
\begin{enumerate}
\item The rabbit moves invisibly to a point $A_n$ such that the distance between $A_{n-1}$ and $A_n$ is exactly 1.
\item A tracking device reports a point $P_n$ to the hunter. The only guarantee provided by the tracking device to the hunter is that the distance between $P_n$ and $A_n$ is at most 1.
\item The hunter moves visibly to a point $B_n$ such that the distance between $B_{n-1}$ and $B_n$ is exactly 1.Is it always possible, no matter how the rabbit moves, and no matter what points are reported by the tracking device, for the hunter to choose her moves so that after 109 rounds she can ensure that the distance between her and the rabbit is at most 100?
\end{enumerate}

\item An integer N $\geq$ 2 is given. A collection of N(N+1) soccer players, no two of whom
are of the same height, stand in a row. Sir Alex wants to remove N(N-1) players from this row
leaving a new row of 2N players in which the following N conditions hold:
\begin{enumerate}
\item no one stands between the two tallest players,
\item no one stands between the third and fourth tallest players,
\item (N) no one stands between the two shortest players.
\end{enumerate}
Show that this is always possible.
