\renewcommand{\theequation}{\theenumi}
\begin{enumerate}[label=\arabic*.,ref=\thesubsection.\theenumi]
\numberwithin{equation}{enumi}
\item Find the length of the latus rectum, the eccentricity and the coordinates of the
foci of the ellipses
\begin{enumerate}
\item 
$
\vec{x}^T\myvec{4 & 0\\0& 9}\vec{x} = 36
$
\item 
$
\vec{x}^T\myvec{9 & 0\\0& 4}\vec{x} = 36
$
\item
$
\vec{x}^T\myvec{1 & 0\\0& 2}\vec{x} = 8
$
\end{enumerate}
\item Find the equation of the ellipse whose foci are the points $\myvec{3\\0}$,  $\myvec{-3\\0}$
and eccentricity $\frac{1}{2}$.  What are the equations of the directrices?
\item Find the equation of the ellipse of eccentricity $\frac{3}{4}$, which has its centre at the point $\myvec{4\\0}$ and touches the axis of $y$ at the
origin.  What is the length of its latus rectum?
\item An ellipse has the axis of $y$ for directrix and its centre at the point $\myvec{6\\0}$.   Find its 
equation if its eccentricity is $\frac{3}{4}$.
\item Find the equation of the ellipse which has a focus at $\myvec{3\\1}$, corresponding directrix the line
\begin{align}
\myvec{1 & 0}\vec{x} = 6
\end{align}
and
eccentricity $\frac{1}{2}$.  What are the lengths of its axes?
\item An ellipse has its centre at $\myvec{2\\3}$ and a focus at $\myvec{3\\4}$ and its eccentricity is $\frac{1}{2}$.  Find its equation.
\item Are the points $\myvec{2\\1}$, $\myvec{3\\-2}$ inside or outside the ellipse
\begin{align}
\vec{x}^T\myvec{2 & 0\\0& 5}\vec{x} = 20
\end{align}
\item Prove that the line $y=x-5$ touches the ellipse
\begin{align}
\vec{x}^T\myvec{9 & 0\\0& 16}\vec{x} = 144
\end{align}
and find the coordinates of the point of contact.
\item The line 
\begin{align}
\myvec{2 & 3}\vec{x} = c
\end{align}
 touches the ellipse 
\begin{align}
\vec{x}^T\myvec{4 & 0\\0& 9}\vec{x} = 1
\end{align}
  Find the values of $c$.
\item Find the equation of the tangent to the ellipse 
\begin{align}
\vec{x}^T\myvec{1 & 0\\0& 4}\vec{x} = 8
\end{align}
 at the point $\myvec{2\\1}$, and also the equations of the two tangents perpendicular to this.
\item Find the equations of the tangents to the ellipse 
\begin{align}
\vec{x}^T\myvec{3 & 0\\0& 4}\vec{x} = 2
\end{align}
 which makes an angle of $60\degree$ with the major axis.
\item Find at what point the line 
\begin{align}
\myvec{e & 1}\vec{x} = a
\end{align}
touches the ellipse
\begin{align}
\vec{x}^T\myvec{1-e^2 & 0\\0& 1}\vec{x} = a^2\brak{1-e^2}
\end{align}
\item Prove that the normal at an end of the latus rectum meets the major axis at a distance $ae^3$ from the centre.
\item Prove that the normal at an end $L$ of the latus rectum meets the minor axis in $g$, and $l$ is the projection of $L$ on the
minor axis, then
\begin{align}
gl=a
\end{align}
\item Prove that the normal at $\myvec{x\\y}$ divides the major axis into segments of lengths $a-e^2x$ and $a+e^2x$.
\item Prove that if the normal at $\vec{P}$ meets the major axis in $\vec{G}$, and the minor axis in $\vec{G}_1$, then
\begin{enumerate}
\item $SG=eSP;$
\item $PG:PG_1 = b^2:a^2$
\end{enumerate}

\end{enumerate}
