\begin{enumerate}[1.]
\item Find the length of the latus rectum, the eccentricity and the coordinates of the
foci of the ellipses
\begin{enumerate}[(i)]
\item 
$
4x^2+9y^2=36
$
\item 
$
9x^2+4y^2=36
$
\item
$
x^2+2y^2=8
$
\end{enumerate}
\item Find the equation of the ellipse whose foci are the points $\brak{3,0}$,  $\brak{-3,0}$
and eccentricity $\frac{1}{2}$.  What are the equations of the directrices?
\item Find the equation of the ellipse of eccentricity $\frac{3}{4}$, which has its centre at the point $\brak{4,0}$ and touches the axis of $y$ at the
origin.  What is the length of its latus rectum?
\item An ellipse has the axis of $y$ for directrix and its centre at the point $\brak{6,0}$.   Find its 
equation if its eccentricity is $\frac{3}{4}$.
\item Find the equation of the ellipse which has a focus at $\brak{3,1}$, corresponding directrix the line $x=6$ and
eccentricity $\frac{1}{2}$.  What are the lengths of its axes?
\item An ellipse has its centre at $\brak{2,3}$ and a focus at $\brak{3,4}$ and its eccentricity is $\frac{1}{2}$.  Find its equation.
\item Are the points $\brak{2,1}$, $\brak{3,-2}$ inside or outside the ellipse
\begin{align*}
2x^2+5y^2-20 = 0
\end{align*}
\item Prove that the line $y=x-5$ touches the ellipse
\begin{align*}
9x^2+16y^2=144,
\end{align*}
and find the coordinates of the point of contact.
\item The line $2x+3y=c$ touches the ellipse $4x^2+9y^2=1$.  Find the values of $c$.
\item Find the equation of the tangent to the ellipse $x^2+4y^2=8$ at the point $\brak{2,1}$, and also the equations of the two tangents perpendicular to this.
\item Find the equations of the tangents to the ellipse $3x^2+4y^2=2$ which makes an angle of $60\degree$ with the major axis.
\item Find at what point the line $y+ex=a$ touches the ellipse
\begin{align*}
x^2\brak{1-e^2}+y^2=a^2\brak{1-e^2}
\end{align*}
\item Prove that the normal at an end of the latus rectum meets the major axis at a distance $ae^3$ from the centre.
\item Prove that the normal at an end $L$ of the latus rectum meets the minor axis in $g$, and $l$ is the projection of $L$ on the
minor axis, then
\begin{align*}
gl=a
\end{align*}
\item Prove that the normal at $\brak{x,y}$ divides the major axis into segments of lengths $a-e^2x$ and $a+e^2x$.
\item Prove that if the normal at $P$ meets the major axis in $G$, and the minor axis in $G_1$, then
\begin{enumerate}[(i)]
\item $SG=eSP;$
\item $PG:PG_1 = b^2:a^2$
\end{enumerate}

\end{enumerate}