\renewcommand{\theequation}{\theenumi}
\begin{enumerate}[label=\arabic*.,ref=\thesubsection.\theenumi]
\numberwithin{equation}{enumi}
\item  Equal chords of a circle (or of congruent circles) subtend equal angles at the centre. 
\item  If the angles subtended by two chords of a circle (or of congruent circles) at the centre (corresponding centres) are equal, the chords are equal.
\item  The perpendicular from the centre of a circle to a chord bisects the chord. 
\item  The line drawn through the centre of a circle to bisect a chord is perpendicular to the chord.
\item  There is one and only one circle passing through three non-collinear points. 
\item  Equal chords of a circle (or of congruent circles) are equidistant from the centre (or corresponding centres).
\item Chords equidistant from the centre (or corresponding centres) of a circle (or of congruent circles) are equal.
\item  If two arcs of a circle are congruent, then their corresponding chords are equal and conversely if two chords of a circle are equal, then their corresponding arcs (minor, major) are congruent.
\item Congruent arcs of a circle subtend equal angles at the centre. 
\item  The angle subtended by an arc at the centre is double the angle subtended by it at any point on the remaining part of the circle.
\item Angles in the same segment of a circle are equal. \item  Angle in a semicircle is a right angle. 
\item  If a line segment joining two points subtends equal angles at two other points lying on the same side of the line containing the line segment, the four points lie on a circle. 
\item  The sum of either pair of opposite angles of a cyclic quadrilateral is 180$\degree$.
\item  If sum of a pair of opposite angles of a quadrilateral is 180$\degree$, the quadrilateral is cyclic.
%
\item AB is a diameter of the circle, $CD$ is a chord equal to the radius of the circle. $AC$ and $BD$ when extended intersect at a point $E$. Prove that $\angle AEB = 60\degree$.
\item $ABCD$ is a cyclic quadrilateral in which $AC$ and $BD$ are its diagonals. If $\angle DBC = 55\degree$ and $\angle BAC = 45\degree$, find $\angle BCD$
\item Two circles intersect at two points $A and B$. $AD$ and $AC$ are diameters to the two circles (see Fig.10.34). Prove that $B$ lies on the line segment $DC$.
\item Prove that the quadrilateral formed (if possible) by the internal angle bisectors of any quadrilateral is cyclic.

\end{enumerate}
