\renewcommand{\theequation}{\theenumi}
\begin{enumerate}[label=\arabic*.,ref=\thesubsection.\theenumi]
\numberwithin{equation}{enumi}
\item Find the remainder when $x^3-ax^2 +6x-a$ is divided by $x-a$.
\item Find the value of k, if x – 1 is a factor of p(x) in each of the following cases: 
\begin{enumerate}
\item $p(x) = x^2 + x + k$
\item $p(x) = kx^2-\sqrt{2}x+1$
\item $p(x) = 2x^2 + kx + \sqrt{2}$
\item $p(x) = kx^2  - 3x + k$
\end{enumerate}
\item Divide the polnyomial $p(x)$ by the polynomial $g(x)$ and find the quotient and remainder in each of the following:
\begin{enumerate}
\item $p(x) = x^3-3x^2+5x-3, g(x) = x^2-2$.
\item $p(x) = x^4-3x^2+4x+5, g(x) = x^2+1-x$.
\item $p(x) = x^4-5x+6, g(x) = 2-x^2$.
\end{enumerate}
\item Check whether the first polynomial is a factor of the second polynomial by dividing the second polynomial by the first polynomial:
\begin{enumerate}
\item $t^2-x,2t^4+3t^3-2t^2-9t-12$.
\item $x^2+3x+1, 3x^4+5x^3-7x^2+2x+2$.
\item $x^3-3x+1, x^5-4x^3+x^2+3x+1$.
\end{enumerate}
%
\item Obtain all the other zeroes of $3x^4+6x^3-2x^2-10x-5$, if two of its zeroes are $\sqrt{\frac{5}{3}}$and $-\sqrt{\frac{5}{3}}$.
\item On dividing $x^3-3x^2+x+2$ by a polynomial $g(x)$, the quotient and remainder were $x-2$ and $-2x+4$respectively.  Find $g(x)$.
\item Verify that the numbers given alongside the cubic polynomials below are their zeroes.  Also verify if the relationship between the zeroes and the coefficients in each case:
\begin{enumerate}
\item $2x^3+x^2-5x+2; \frac{1}{2}, 1, -2$
\item $x^3-4x^2+5x-2; 2, 1, 1$
\end{enumerate}
\item Find a cubic polynomial with the sum, sum of the product of its zeroes taken two at a time, and the product of its zeroes as 2, -7, -4 respectively.
\item If two zeroes of the polynomial $x^4-6x^3-26x^2+138x-35$ are $2\pm \sqrt{3}$, find the other zeroes.\item If the polynomial $x^4-6x^3+16x^2-25x+10$ is divided by another polynomial $x^2-2x+k$, the remainder comes out to be $x+a$, find $k$ and $a$.
\item The area of a rectangular plot is 528 $m^2$
. The length of the plot (in metres) is one more than twice its breadth. We need to find the length and breadth of the plot.
\item The product of two consecutive positive integers is 306. We need to find the integers.
\item Rohan’s mother is 26 years older than him. The product of their ages (in years) 3 years from now will be 360. We would like to find Rohan’s present age.
\item A train travels a distance of 480 km at a uniform speed. If the speed had been 8 km/h less, then it would have taken 3 hours more to cover the same distance. We need to find the speed of the train.
\item Find two numbers whose sum is 27 and product is 182. 
\item  Find two consecutive positive integers, sum of whose squares is 365. 
\item  The altitude of a right triangle is 7 cm less than its base. If the hypotenuse is 13 cm, find the other two sides.
\item  A cottage industry produces a certain number of pottery articles in a day. It was observed on a particular day that the cost of production of each article (in rupees) was 3 more than twice the number of articles produced on that day. If the total cost of production on that day was \rupee 90, find the number of articles produced and the cost of each article.\item The sum of the reciprocals of Rehman’s ages, (in years) 3 years ago and 5 years from now is $\frac{1}{3}$.  Find his present age.
\item In a class test, the sum of Shefali’s marks in Mathematics and English is 30. Had she got 2 marks more in Mathematics and 3 marks less in English, the product of their marks would have been 210. Find her marks in the two subjects.
\item The diagonal of a rectangular field is 60 metres more than the shorter side. If the longer side is 30 metres more than the shorter side, find the sides of the field.
\item The difference of squares of two numbers is 180. The square of the smaller number is 8 times the larger number. Find the two numbers.
\item A train travels 360 km at a uniform speed. If the speed had been 5 km/h more, it would have taken 1 hour less for the same journey. Find the speed of the train.
\item Two water taps together can fill a tank in 9$\frac{3}{ 8}$
hours. The tap of larger diameter takes 10
hours less than the smaller one to fill the tank separately. Find the time in which each tap can separately fill the tank.
\item An express train takes 1 hour less than a passenger train to travel 132 km between Mysore and Bangalore (without taking into consideration the time they stop at intermediate stations). If the average speed of the express train is 11km/h more than that of the passenger train, find the average speed of the two trains.
\item Sum of the areas of two squares is 468 $m^22$ find the sides of the two squares.
\item Find the values of k for each of the following quadratic equations, so that they have two equal roots:
\begin{enumerate}
\item 	$2x^2+kx+3 = 0$
\item 	$kx\brak{x-2}+6= 0$
\end{enumerate}
\item Is it possible to design a rectangular mango grove whose length is twice its breadth, and the area is 800 $m^2$
? If so, find its length and breadth.
\item Is the following situation possible? If so, determine their present ages. The sum of the ages of two friends is 20 years. Four years ago, the product of their ages in years was 48.
\item Is it possible to design a rectangular park of perimeter 80 m and area 400 $m^2$ its length and breadth
\end{enumerate}
