\renewcommand{\theequation}{\theenumi}
\begin{enumerate}[label=\arabic*.,ref=\thesubsection.\theenumi]
\numberwithin{equation}{enumi}
%
\item Divide $p(x)$ by $g(x)$, where $p(x) = x + 3x^2– 1$ and $g(x) = 1 + x$.
\item Divide the polynomial $p(x) = 3x^4-4x^3-3x-1 $ by $x-1$.
\item Find the value of $k$, if $x – 1$ is a factor of $p(x) = 4x^3+ 3x^2 - 4x + k$.
%
\item Divide $2x^2+3x+1$ by $x+2$.
\item Divide $3x^3+x^2+2x+5$ by $1+2x+x^2$.
\item Find all the zeroes of $2x^4-3x^3-3x^2+6x-2$, if you know that two of its zeroes are $\sqrt{2}$ and $-\sqrt{2}$.
\item John and Jivanti together have 45 marbles. Both of them lost 5 marbles each, and the product of the number of marbles they now have is 124. We would like to find out how many marbles they had to start with.
\item  A cottage industry produces a certain number of toys in a day. The cost of production of each toy (in rupees) was found to be 55 minus the number of toys produced in a day. On a particular day, the total cost of production was \rupee 750. We would like to find out the number of toys produced on that day.
\item The product of Sunita’s age (in years) two years ago and her age four years from now is one more than twice her present age. What is her present age?
\item Find two consecutive odd positive integers, sum of whose squares is 290.
\item A rectangular park is to be designed whose breadth is 3 m less than its length. Its area is to be 4 square metres more than the area of a park that has already been made in the shape of an isosceles triangle with its base as the breadth of the rectangular park and of altitude 12 m. Find its length and breadth.
\item A motor boat whose speed is 18 km/h in still water takes 1 hour more to go 24 km upstream than to return downstream to the same spot. Find the speed of the stream.
\item A pole has to be erected at a point on the boundary of a circular park of diameter 13 metres in such a way that the differences of its distances from two diametrically opposite fixed gates A and B on the boundary is 7 metres. Is it possible to do so? If yes, at what distances from the two gates should the pole be erected?
\item The focus of a parabolic mirror is at a distance of 5 cm from its vertex. If the mirror is 45 cm deep, find the distance AB .
\item A beam is supported at its ends by  supports which are 12 metres apart. Since the load is concentrated at its centre, there is a deflection of 3 cm at the centre and the deflected beam is in the shape of a parabola. How far from the centre is the deflection 1 cm?
\item 19 A rod AB of length 15 cm rests in between two coordinate axes in such a way that the end point $\vec{A}$ lies on x-axis and end point $\vec{B}$ lies on y-axis. A point $\vec{P}$ is taken on the rod in such a way that $AP$ = 6 cm. Show that the locus of P is an ellipse
\end{enumerate}
