\begin{enumerate}[1.]
\item Without drawing a figure determine whether the points $\brak{-1,2}$, $\brak{0,0}$, $\brak{3,-4}$ lie outside, on the circumference, or inside the circle
\begin{align*}
x^2+y^2-5x+2y-5 = 0
\end{align*}
\item Find the points of intersection of the line $3x+2y=12$ and the circle $x^2+y^2=13$ and find for what values of $c$ the line $3x+2y=c$ touches the circle.
\item Prove that the line $3x+2y=30$ touches the circle
\begin{align*}
x^2+y^2-10x-2y+13 = 0
\end{align*}
and find the coordinates of the point of contact.
\item For what values of $m$ does the line $y=mx$ touch the circle
\begin{align*}
x^2+y^2-6x-2y+8 = 0
\end{align*}
\item Prove that the circle $\brak{x-a}^2+\brak{y-a}^2=a^2$ touches the coordinate axes.
\item Show that two circles can be drawn to pass through the point $\brak{1,2}$ and touch the coordinate axes, and find their equations.
\item Find the length of the tangent from the point $\brak{7,4}$ to the circle 
\begin{align*}
x^2+y^2-4x-6y+12 = 0
\end{align*}
\item  Find the equations of the tangents to the circle
\begin{align*}
x^2+y^2 -4x -3y+5 = 0
\end{align*}
that are parallel to the line $y+x=0$.
\item Find the equations of the tangents to the circle
\begin{align*}
x^2+y^2-7x-5y+18=0
\end{align*}
at the points $\brak{4,3}$ and $\brak{3,2}$, showing that they are parallel.
\item Find the equations of the tangent and normal to the circle
\begin{align*}
x^2+y^2-6x+4y-12=0
\end{align*}
at the point $\brak{6,2}$.
\item Prove that the line $x+y=1$ touches the circle
\begin{align*}
x^2+y^2-8x-6y+7 = 0
\end{align*}
and find the equations of the parallel and perpendicular tangents.
\item Find the equation of the tangent at the origin to the circle
\begin{align*}
x^2+y^2+2gx+2fy=0
\end{align*}
\item Prove that the line $x\cos\alpha+y\sin\alpha = p$ touches the circle
\begin{align*}
\brak{x-a}^2+\brak{y-b}^2 = r^2
\end{align*}
if
\begin{align*}
r = \pm \brak{p-a\cos\alpha-b\sin\alpha}
\end{align*}
\item Find the points of contact of the tangents to the circle
\begin{align*}
x^2+y^2=25
\end{align*}
that pass through the point $\brak{7,1}$ and write down the equations of the tangents.
\item Prove that the tangent to the circle $x^2+y^2=5$ at the point $\brak{1,-2}$ also touches the circle
\begin{align*}
x^2+y^2-8x+6y+20=0
\end{align*}
and find the coordinates of the point of contact.
\item Find the equations of the circles that touch the lines
\begin{align*}
y=0, y=4, 2x+y = 2
\end{align*}
\item Find the coordinates of the middle point of the chord
\begin{align*}
x+7y=25
\end{align*}
of the circle
\begin{align*}
x^2+y^2=25
\end{align*}
\item Find the equation of the chord of the circle
\begin{align*}
x^2+y^2-6x-4y-23 = 0
\end{align*}
which has the point $\brak{4,1}$ as its middle point.
\item Prove that the circle
\begin{align*}
x^2+y^2-6x-4y+9 = 0
\end{align*}
subtends an angle $\tan^{-1}\frac{12}{5}$ at the origin.
\item Find the condition that the line
\begin{align*}
lx+my+n = 0
\end{align*}
should touch the circle
\begin{align*}
\brak{x-a}^2+\brak{y-b}^2 = r^2
\end{align*}
\item Verify that the perpendicular bisector of the chord joining two points $\brak{x_1,y_1}$, $\brak{x_2,y_2}$ on the circle
\begin{align*}
x^2+y^2+2gx+2fy+c = 0
\end{align*}
passes through the centre.
\end{enumerate}