%\begin{enumerate}[1.]
%\numberwithin{equation}{\thesubsection.enumi}

%\begin{enumerate}[label=\arabic*.,ref=\thesection]
\renewcommand{\theequation}{\theenumi}
\begin{enumerate}[label=\arabic*.,ref=\thesubsection.\theenumi]
%\begin{enumerate}[label=\arabic*.,ref=\thesubsection.\theenumi]
%\numberwithin{equation}{subsection}

%\begin{enumerate}[label=\arabic*.,ref=\thesubsection.\theenumi]
%\begin{enumerate}[label=\thesection.\arabic*,ref=\thesection.\theenumi]

%\numberwithin{equation}{enumi}
\item Find the distance between 
\begin{align}
\vec{P} = \myvec{-2\\4}, \vec{Q} = \myvec{3\\-5}
\end{align}
%Mark on a diagram the points $\myvec{-2,4}, \myvec{3,-5}$ and find the distance between them.
\solution
\input{./solutions/1/1/1/solution.tex}
%
\item
Find the length of $PQ$ for
\begin{enumerate}
\item $\vec{P}=\myvec{-1\\1}$ and $\vec{Q}=\myvec{2\\-1}$;
\item $\vec{P}=\myvec{4\\3}$ and $\vec{Q}=\myvec{-2\\2}$;
\item $\vec{P}=\myvec{a\\b}$ and $\vec{Q}=\myvec{-b\\a}$.
\end{enumerate}

\item Using direction vectors, show that  $\myvec{2\\1}, \myvec{4\\7}, \myvec{5\\4}$ and $\myvec{1\\4}$ are the vertices of a parallelogram.
\item Using Baudhayana's theorem, show that the points $\myvec{-3\\-4}, \myvec{2\\6}$ and $\myvec{-6\\10}$  are the vertices of a right-angled
traingle.  Repeat using orthogonality.
\item Plot the points $\myvec{0\\2},\myvec{1\\1},\myvec{4\\4}\text{ and }\myvec{3\\5}$ and prove that they are the vertices of a rectangle.
\item Show that $\vec{B}=\myvec{-2\\-2},\vec{A}=\myvec{-1\\2}\text{ and }\vec{C}=\myvec{3\\1}$ are the vertices of an isosceles triangle.
\item In the last question, find the distance of the vertex $\vec{A}$ of the triangle from the middle point of the base $BC$.
\item Prove that the points $\myvec{-1\\0}$, $\myvec{0\\3}$, $\myvec{3\\2}$ and $\myvec{2\\-1}$ are the vertices of a square.
\item Prove that the points $\vec{A}=\myvec{-1\\0}$, $\vec{B}=\myvec{3\\1}$, $\vec{C}=\myvec{2\\2}$  and $\vec{D}=\myvec{-2\\1}$ are the vertices of a parallelogram.  Find $\vec{E},\vec{F},\vec{G},\vec{H}$, the mid points of $AB, BC, CD, AD$ respectively.  Show that EG and FH bisect each other.
\item Prove that the points $\myvec{21\\-2}$, $\myvec{15\\10}$, $\myvec{-5\\0}$  and $\myvec{1\\-12}$ are the vertices of a rectangle, and find the
coordinates of its centre.
\item Find the lengths of the medians of the triangle whose vertices are at the points $\myvec{1\\2}$, $\myvec{0\\3}$ and $\myvec{-1\\-2}$.
\item Find the coordinates of the points that divide the line joining the points $\myvec{-35\\-20}$ and $\myvec{5\\-10}$ into four equal parts.
\item Find the coordinates of the points of trisection of the line joining the points $\myvec{-5\\5}$ and $\myvec{25\\10}$.
\item Prove that the middle point of the line joining the points $\myvec{-5\\12}$ and $\myvec{9\\-2}$ is a point of trisection of the line
joining the points $\myvec{-8\\-5}$ and $\myvec{7\\10}$.
\item The points $\myvec{8\\5}$, $\myvec{-7\\-5}$ and $\myvec{-5\\5}$ are three of the vertices of a parallelogram.  Find the coordinates of
the remaining vertex which is to be taken as opposite to $\myvec{-7\\-5}$.
\item The point $\myvec{2\\6}$ is the intesection of the diagonals of a parallelogram two of whose vertices are at the points $\myvec{7\\16}$ and $\myvec{10\\2}$.
Find the coordinates of the remaining vertices.
\item Find the area of the triangle whose vertices are the points $\myvec{2\\3}$, $\myvec{-4\\7}$ and $\myvec{5\\-2}$.  
\item Find the coordinates of  points which divide the join of $\myvec{2\\3}$, $\myvec{-4\\5}$ externally in the ratio $2:3$, and also
externally in the ratio $3:2$.
\item Prove the centroid of $\triangle ABC$ is
\begin{equation}
\vec{O}=\frac{\vec{A}+\vec{B}+\vec{C}}{3}
\end{equation}

\end{enumerate}
%\bibliography{IEEEabrv,gvv_opt}

%\input{./chapters/chapter2} 
%%
%\newpage
%\section{$M$-ary Modulation}
%\input{./chapters/chapter3} 
%
%\newpage
%\section{BER in Rayleigh Flat Slowly Fading Channels}
	%\input{./chapters/chapter4} 




