\renewcommand{\theequation}{\theenumi}
\begin{enumerate}[label=\arabic*.,ref=\thesubsection.\theenumi]
\numberwithin{equation}{enumi}
\item Prove that the circle of centre $\brak{3,4}$ and rdius 5 passes
through the origin.  Find the equations of the tangent at the origin 
and of the parallel tangent.  IN what other points does the circle
cut the axes?
\item find the equation of a circle having the points $\brak{2,1}$
and $\brak{1,-3}$ for the ends of a diameter.  find
the coordinates of the ends of the perpendicular diameter.
\item Find the equation of the tangent to the circle $x^2+y^2=1$
at the point $\brak{\frac{4}{5},\frac{3}{5}}$.  Find the two points
in which this tangent cuts the axes and also find the equations of the other
tangents to the circle that can be drawn from the last two points.
\item For what values of $k$ does the line $y=kx$ touch the circle
$x^2+y^2+2x+4y+1=0$?  find the coodinates of the points of contact.
\item Show that the points $\brak{5,8}$ and $\brak{-1,0}$ are the opposite
ends of a diameter of the circle $x^2+y^2-4x-8y-5=0$.  Find the equations
of the tangents at these points.
\item Find the equation of the circle through the points $\brak{3,0},\brak{4,0}$
and $\brak{1,2}$.  Find the equation of the tangent at the point $\brak{3,13}$.
\item Find the equation of the circle which passes through the points
$\brak{3,0}$, $\brak{0,4}$, $\brak{0,6}$.  In what other points does the circle
cut the $x$-axis?
\item Find where the line $x+y=5$ cuts the circle 
\begin{equation}
3x^2+3y^2-11x-11y+16=0?
\end{equation}
What are the equations of the tangents parallel to the line?
\item Find the coordinaes of the points in which the line $x+2y=7$ cuts the
circle $x^2+y^2-13x-13y+52=0$.  Find the equations of the tangents at these
points and the coordinates of the point in which these tangents intersect.
\item Prove that if $\brak{x_1,y_1}$ is the middle point of a chord of a circle
$x^2+y^2=a^2$, then the equation of the chord is $xx_1+yy_1 = x_1^2+y_1^2$.  
\item Find the coordinates of the middle point of the chord of the circle
$x^2+y^2=25$ which lies along the line $3x-4y=7$.  Also find the 
points of contact of the parallel tangents.
\item Find the coordinates of the middle point of the chord of the circle
$x^2+y^2-4x+6y+1=0$ which lies along the line $2x-3y=12$.  
\item Prove that the line $2x+y-7=0$ is the equation of a diameter of the circle
$x^2+y^2-6x-2y+5=0$, and find the equations of the tangents at the ends of this
diameter.
\item Find the angle which the circle $x^2+y^2-6x-4y+9=0$ subtends at
the origin.
\item Find the equations of the circles which pass through the point $\brak{-2,1}$
and touch both the coordinate axes.
\item Prove that the locus of points at which the circle
\begin{equation}
x^2+y^2-4x-6y+4=0
\end{equation}
subtends a right angle is the circle $x^2+y^2-4x-6y-5=0$.
\item Find the equations of the tangents to the circle
\begin{equation}
x^2+y^2-4x+2y-8=0
\end{equation}
which are parallel to the line $2x+3y=c$.
\item Find the equation of the chord of the circle
\begin{equation}
x^2+y^2-4x+2y-4=0
\end{equation}
which has $\brak{3,1}$ as its middle point.
\item Show that the points $\brak{0,0}$, $\brak{2,1}$, $\brak{3,3}$
and $\brak{1,2}$ are the corners of a rhombus, and find the equation
of its inscribed circle.
\item Find the equation of the circle which has the same centre as the circle
$x^2+y^2+6x-10y+18=0$ and passes through the point $\brak{6,7}$.  Show that
the origin is outside the given circle and inside the other.
\item Find the locus of the centre of a circle
\begin{equation}
x^2+y^2+2gx+2fy+c=0
\end{equation}
which is such that the tangets drawn to the circle from the origin are always at right angles.
\end{enumerate}
