\renewcommand{\theequation}{\theenumi}
\begin{enumerate}[label=\arabic*.,ref=\thesubsection.\theenumi]
\numberwithin{equation}{enumi}
\item Prove that, if a variable line moves with its ends on the coordinate axes so as
to enclose with them a constant area, then the locus of the middle point of the line
is a rectangular hyperbola.
\item Prove that, if a straight line moves with its ends on the coordinate axes so as
to form with them a triangle of constant area $c^2$, then the line touches the rectangular
hyperbola $2xy=c^2$.
\item Find the value of $c^2$ if the rectangular hyperbola $xy=c^2$ touches the line $3x+5y=80$.
\item Show that the equation of the tangent at $\brak{x_1,y_1}$  on the rectangular hyperbola
$xy=c^2$ may be put in the form $\frac{x}{x_1}+\frac{y}{_1} = 2$.
\item Prove that the line $3x+4y=24c$ touches the hyperbola $xy=12c^2$.  What is the area of the 
triangle whose sides are the asymptotes and this tangent?
\item Find the points in which the line $2x+y=3c$ cuts the hyperbola $xy=c^2$, showing that
one of the points of intersecton lies on the transverse axis of the hyperbola.
\item Prove that, if $a$ and $b$ are real numbers of opposite signs, the straight line
$ax+by=1$ cannot touch the rectangular hyperbola $xy=c^2$.
\item Prove that the straight line $x+t^2y=2ct$ is a tangent to the rectangular hyperbola
$xy=c^2$, and that no perpendicular line can touch the curve.
\item Prove that, if through any point on the curve $xy=c^2$ two perpendicular lines
are drawn, their other intersections with the curve will lie on opposite
brances.
\item The normal at $P \brak{3,4}$ on the rectangular hyperbola $xy=12$ meets the curve again at $Q$.
Prove that $PQ = \frac{125}{12}$.
\item Find the equations of the tangent and normal at the point $x=4ct$, $y=\frac{3c}{t}$ on the rectangular
hyperbola $xy=12c^2$.  Verify that the length of the tangent intercepted by the asymptotes is bisected
at the point of contact.
\item Find the equation of the tangent at the point $x=2ct$, $y=\frac{5c}{t}$ on the hyperbola $xy=10c^2$, and show 
that the area of the triangle the tangent forms with the asymptotes is independent of $t$.
\item Find the equation of the chord joining the points $\brak{ct_1,\frac{c}{t_1}}$ and $\brak{ct_2\frac{c}{t_2}}$ on the rectangular 
hyperbola $xy=c^2$.  Find the equation of the tangent parallel to the chord, and the coordinates
of its point of contact.
\item Show that the hyperbola $x^2-y^2=20$ and $xy=24$ cut at right angles at all the common points.
\item If the line $2x-ky=8$ touches a rectangular hyperbola $xy=9$, what is the value of $k$, and
what are the coordinates of the point of contact?
\item Find the coordinates of the foci and the equations of the directrices of the 
hyperbola $xy=c^2$, referred to the asymptotes as axes.
\item A circle cuts the rectangular hyperbola $xy=1$ in the points $\brak{x_r,y_r}$, $r=1,2,3,4$.  Prove 
that $x_1x_2x_3x_4 = y_1y_2y_3y_4=1$.
\item Find the points of intersection of the line $8y-2x=15c$ and the rectangular hyperbola $xy=c^2$.  Prove
that the line is a normal to the curve at one of these intersections.
\item Prove that the normal at the point $P \brak{ct,\frac{c}{t}}$ on the rectangular hyperbola $xy=c^2$
meets the curve again at $Q$ so that
\begin{equation}
PQ=c\brak{t^2+\frac{1}{t^2}}^{\frac{3}{2}}
\end{equation}
\item Four points are taken on a rectangular hyperbola $xy=c^2$.  Find the condition that
the chord joining two of the points should be perpendicular to the chord joining
the other two.  Prove that, if the condition is satisfied for one pair of such chords, then
it is true for all three pairs.
\item Prove that the locus of the middle points of chords of the rectangular
hyperbola $xy=c^2$ which pass through the point $\brak{2c,2c}$ is an equal hyperbola and find the coordinates
of its vertices.
\item The radius $OP$ from the centre to a point $P$ on the rectangular hyperbola $xy=c^2$ makes
an angle $\theta$ with the $x$-axis, and the normal at $P$ cuts the axes of $x$ and $y$ in $G$ and $G_1$.
Prove that $\frac{PG}{PG_1}=\tan^2\theta$.
\end{enumerate}
