\item How many positive integers less than 1000 have the property that the sum of the digits of each such number is divisible by 7 and the number itself is divisible by 3?

\item A contractor has two teams of workers: team A and team B. Team A can complete a job in 12 days and team B can do the same job in 36 days. Team A starts working on the job and team B joins team A after four days. The team A withdraws after two more days. For how many more days should team B work to complete the job? 

\item A pen costs /Rs.11 and a notebook costs 13. Find the number of ways in which a person can spend exactly 1000 to buy pens and notebooks. 

\item There are ﬁve cities A, B, C, D, E on a certain island. Each city is connected to every other city by road. In how many ways can a person starting from city A come back to A after visiting some cities without visiting a city more than once and without taking the same road more than once? (The order in which he visits the cities also matters: e.g., the routes $A\rightarrow B\rightarrow C \rightarrow A$ and $A \rightarrow C \rightarrow B \rightarrow A$ are different.)

\item There are eight rooms on the ﬁrst ﬂoor of a hotel, with four rooms on each side of the corridor, symmetrically situated (that is each room is exactly opposite to one other room). Four guests have to be accommodated in four of the eight rooms (that is, one in each) such that no two guests are in adjacent rooms or in opposite rooms. In how many ways can the guests be accommodated?

\item Let $f(x) = \sin\frac{x}{3} + \cos\frac{3x}{10}$ for all real x. Find the least natural number n such that 
$f(n\pi + x) = f(x)$ for all real x.

\item In a class, the total numbers of boys and girls are in the ratio $4 : 3$. On one day it was found that 8 boys and 14 girls were absent from the class, and that the number of boys was the square of the number of girls. What is the total number of students in the class?

\item Five distinct 2-digit numbers are in a geometric progression. Find the middle term.

\item Suppose the altitudes of a triangle are 10, 12 and 15. What is its semi-perimeter?

\item  For each positive integer n, consider the highest common factor $h_{n}$ of the two numbers n! + 1 and (n + 1)!. For 
$n < 100$, ﬁnd the largest value of $h_{n}$.


