\item An ant leaves the anthill for its morning exercise. It walks 4 feet east and then makes a $160^{o}$ turn to the right and walks 4 more feet. It then makes another $160^{o}$  turn to the right and walks 4 more feet. If the ant continues this pattern until it reaches the anthill again, what is the distance in feet it would have walked?

\item Five persons wearing badges with numbers 1, 2, 3, 4, 5 are seated on 5 chairs around a circular table. In how many ways can they be seated so that no two persons whose badges have consecutive numbers are seated next to each other? 
(Two arrangements obtained by rotation around the table are considered different.)

\item How many distinct triangles ABC are there, up to similarity, such that the magnitudes of angles A, B and C in degrees are positive integers and satisfy
\begin{align*}
\cos A \cos B + \sin A \sin B \sin kC = 1
\end{align*}
for some positive integer k, where kC does not exceed $360^{o}$?

\item  In how many ways can a pair of parallel diagonals of a regular polygon of 10 sides be selected?

\item A pen costs $13/-$ and a note book costs $17/-$. A school spends exactly $1000/-$ in the year 2017-18 to buy x pens and y note books such that x and y are as close as possible (i.e, $|x - y|$ is minimum). Next year, in 2018-19, the school spends a little more than $10000/-$ and buys y pens and x note books. How much more did the school pay?

\item Consider the set E of all natural numbers n such that when divided by 11, 12, 13, respectively, the remainders, in that order, are distinct prime numbers in an arithmetic progression. If N is the largest number in E, find the sum of digits of N.

\item Consider the set E = $\{5, 6, 7, 8, 9\}$. For any partition $\{A, B\}$ of E, with both A and B non-empty, consider the number obtained by adding the product of elements of A to the product of elements of B. Let N be the largest prime number among these numbers. Find the sum of the digits of N.

\item A 1 $\times$ n rectangle $(n \geq 1)$ is divided into n unit (1 $\times$ 1) squares. Each square of this rectangle is coloured red, blue or green. Let f(n) be the number of colourings of the rectangle in which there are an even number of red squares. What is the largest prime factor of $f(9)/f(3)$? (The number of red squares can be zero.)

\item A village has a circular wall around it, and the wall has four gates pointing north, south, east and west. A tree stands outside the village, 16m north of the north gate, and it can be just seen appearing on the horizon from a point 48m east of the south gate. What is the diameter, in meters, of the wall that surrounds the village?

\item  We will say that a rearrangement of the letters of a word has no fixed letters if, when the rearrangement is placed directly below the word, no column has the same letter repeated. For instance, HBRATA is a rearrangement with no fixed letters of BHARAT. How many distinguishable rearrangements with no fixed letters does BHARAT have? 
(The two as are considered identical.)
