\begin{enumerate}[1.]
\item Find the distance between the pionts $A$, $B$ whose coordinates are $\brak{3,7}$ and $\brak{11,13}$.  Also
find the coordinates of the point which divides $AB$ in the ratio $3:1$.
\item Find the equations of the sides of a triangle whose corners are at the points
$\brak{3,4}$, $\brak{-3,2}$, $\brak{2,-4}$.
\item In the last problem, find the equations of the perpendiculars from the corners of the triangle
to the opposite sides and verify that they meet in a point.
\item Find the distance between the points $A \brak{2,3}$ and $B \brak{14,8}$.  Find also the equation of the line $AB$ and
the distance from it of the point $C \brak{5,6}$.  What is the area of the triangle $ABC$?
\item The equations of the sides of a triangle are $x+y=5$, $2x-y+4=0$ and $x-4y+4=0$.  Find the tangents of the angles of
the triangle.
\item Find the equation of a line parallel to the line $5x+4y=9$ and making an intercept $-5$ 
on the $x$-axis.
\item Find the equations of two straight lines which pass through the intersection
of the lines $3x+4y=7$, $5x-2y=3$ and are parallel and perpendicular respectively to the line $2x+7y=3$.
\item Find the value of $k$ if the three lines $2x+5y=12$, $7x+2y=11$ and $kx-3y=10$ meet in a point.
\item Prove that the points $\brak{x_1,y_1}$, $\brak{x_2,y_2}$ and
\begin{align*}
\brak{\frac{x_1+kx_2}{1+k},\frac{y_1+ky_2}{1+k}}
\end{align*}
are collinear.
\item Show that the points $\brak{2,3}$ and $\brak{-1,2}$ are on opposite sides of the line $2x-3y=7$.  What are their distances from the line?
\item Two straight lines $AB$, $CD$ bisect one another at right angles.  The coordinates of $A$, $B$ and $C$ are
$\brak{1,5}$, $\brak{3,1}$ and $\brak{-1,1\frac{1}{2}}$.  Find the coordinates of $D$ and the area $ABCD$.
\item Prove that the line $2x+3y=5$ divides the join of the points $\brak{3,-5}$, $\brak{2,1}$ in the ratio $7:1$.
\item Find the equations of the two straight lines which pass through the point $\brak{3,2}$ and make angles of $45\degree$ with the line $4x-5y=6$.
\item Find the equation of the perpendicular bisector of the join of the points $\brak{3,5}$, $\brak{-6,7}$.
\item From a point $A \brak{2,5}$ a perpendicular $AB$ is drawn to the line $3x-4y=8$.  $AB$ is then produced to $C$ so that $BC=3AB$.  Find
the coordinates of $C$.
\item The sides $BC$, $CA$, $AB$ of a triangle have equations $3x+4y=9$, $4x-3y+6=0$, $5x-12y+12=0$.  Find the equations of the
bisectors of the interior angles of the triangle and the coordinates of their point
of concurrence.
\item $ABC$ and $DBC$ are two triangles such that $DB=AB$ and $DC=AC$.  The coordinates of $A$, $B$, $C$
are $\brak{3,1}$, $\brak{2,2}$, $\brak{-1,3}$.  Find the coordinates of $D$.  Also find the equations of $AD$ and $BC$ and verify that these lines are at right angles.
\item Find the centre of the inscribed circle of the triangle formed by the lines $3x-4y+8=0$, $4x+3y-9=0$, $y=6$.
\item Find the equations of two lines passing through the intersection of the lines $x+3y=5$ and $4x-y+2=0$,
and perpendicular and parallel respectively to the line $5x-3y+3=0$.
\item Find the equation of the line which passes through the intersection of the lines $2x+3y=4$ and $3x-y+2=0$
and also through the intersection of the lines $x+y=0$, $4x-y+3=0$.
\item Prove that the points $A \brak{4,2}$ and $C \brak{-3,1}$ subtend a right angle at $B \brak{-\frac{17}{13}, -\frac{20}{13}}$.  Find the coordinates of $D$, the remaining
corner of the rectangle $ABCD$, and verify that $DB=AC$.
\item The points $A \brak{4,2}$, $B \brak{1,-2}$, $C \brak{-3,1}$ and $D$ are the corners of a parallelogram.
Find the coordinates of $D$ and prove that the parallelogram is equal in area to the square on $OD$
where $O$ is the origin.
\item Show that the equation $6x^2+7xy-3y^2+x+7y-2=0$ represents two straight lines, and find the tangents of the angles between then.
\item Find the separate equations of the two straight lines represented by the
equation $x^2-2xy\cosec\theta + y^2 = 0$.  Also find the angles between the lines, and show that these angles are bisected by the lines
$x^2-y^2 = 0$.
\end{enumerate}